---
title: "CFS, 2AFC, Short Study Lists"
author: "pss"
date: "February 10, 2016"
output: pdf_document
---

summary of results for cfs study

Version: presentation in lists of 16. Items studied x3 times 
Note that second/third presentation was in the same order as first presentations
all items studied for total of .5 seconds (including ramping up and down)

these data include subjects that didn't provide many recall choices

```{r, preamble, echo=FALSE}
# preamble

library(ggplot2)
library(plyr)
source("C:/Users/PSadil/Documents/R/fns.R")

setwd("D:/googleDrive/uMass/firstYear/behavioralExpts/pSadil/processDissociation/CFS/cfs_fg/analysisCode/R/afc/shortStudyLists")

```

```{r,data,echo=FALSE,warning=FALSE}
# preliminary changing of folders
#setwd("D:/googleDrive/uMass/firstYear/behavioralExpts/pSadil/processDissociation/CFS/analysisCode/R/afc/shortStudyLists")

wd <- getwd()

dataFile <- paste(wd, "/cfs_obj_2afc_ss1_noCheck.dat", sep="")
# find the data that was generated from the matlab files
data <- read.csv(dataFile)

# add 1 to study resp because participants were instructed to use 0-3

#data[data$studyResp3==1e+05,]$studyResp3 = 1
#data$studyResp3 <- as.factor(data$studyResp3)


nConds = max(data$condition,na.rm=TRUE)
nPAS = max(data[data$studyResp < 1000,]$studyResp,na.rm=TRUE) + 1
nItems = max(data$whichItem,na.rm=TRUE)
nSubs = max(data$subject,na.rm=TRUE)
nTrials = max(data$trial,na.rm=TRUE)
nInCond = nItems / nConds

# number of items in each condition, first presentation
nPerCond = nItems/nConds


data$trial = as.factor(data$trial)
data$whichItem = as.factor(data$whichItem)
data$subject = as.factor(data$subject)
data$condition = as.factor(data$condition)
data$studyResp = as.factor(data$studyResp)
data$studyResp2 = as.factor(data$studyResp2)
data$studyResp3 = as.factor(data$studyResp3)


#data$condition = as.numeric(data$condition)
# don't want PAS as a factor, because there are 
# vastly different numbers of each kind of response
# Do I want condition as factor? if it were, that would
# seem to make stronger claims (justified) about higher levels
# leading to higher recall rates
studyConds <- c("foil","word","cfs","binoc")
cols <- c('black', 'cornflowerblue', 'darkgoldenrod1', 'red')
pasResps <- c("0","1","2","3")

# trim away missing values (there aren't, currently)
data_trim <- na.omit(data)


cutoff = 3 # only look at CFS with PAS 2 or 1
nPresent = 3 # presented 3 times
nStudy = nTrials * nPresent

```


```{r, withinErrorBars, echo=FALSE,warning=FALSE}

# name_pas4 <- withinSubError(data_trim,4,nConds)
# name_pas3 <- withinSubError(data_trim,3,nConds)
# name_pas2 <- withinSubError(data_trim,2,nConds)
# name_pas1 <- withinSubError(data_trim,1,nConds)
# sem <- rbind(name_pas1$sem_cf,name_pas2$sem_cf,name_pas3$sem_cf,name_pas4$sem_cf)
# tPlot <- rbind(name_pas1$y_sj,name_pas2$y_sj,name_pas3$y_sj,name_pas4$y_sj)
# 
# data_plot <- data_trim
# data_plot[data_plot$studyResp3==1e+05,]$studyResp3 = 1
# data_plot$studyResp3 <- as.factor(data_plot$studyResp3)
# #data_plot$studyResp3 == as.double(data_plot$studyResp3)
# 


dfwc3 <- summarySEwithin(data, measurevar="named"
                         , withinvars=c("condition","studyResp3"),
                         idvar="subject", na.rm=FALSE, conf.interval=.95)
dfwc3<-ddply(dfwc3,.(condition),transform,prop=N/sum(N))

dfwc1 <- summarySEwithin(data, measurevar="named"
                         , withinvars=c("condition","studyResp"),
                         idvar="subject", na.rm=FALSE, conf.interval=.95)
dfwc1<-ddply(dfwc1,.(condition),transform,prop=N/sum(N))

```

```{r,named}
dfwc1
dfwc3

```


NOTE: 

1. in these bar graphs, 1e+05 indicates the value that was given to foils (so, there should only be bars over the 1e+05 studyResp for the foil condition).
2. the NA studyResp are missing responses.
3. although these error bars more accurately reflect the within-subjects nature of the study condition factor, the y-axis is still bounded between [0,1]. So, I still need to figure out a reasonable way to plot those values...


```{r,echo=FALSE,warning=FALSE}
ggplot(dfwc3, aes(x=studyResp3, y=named)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  geom_errorbar(width=.25, aes(ymin=named-ci, ymax=named+ci)) +
  facet_grid(. ~ condition ) +
  xlab("PAS") + 
  ylab("named") +
  ggtitle("% named for each condition, given third PAS")

```

```{r,echo=FALSE,warning=FALSE}
ggplot(dfwc3, aes(x=studyResp3, y=prop)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  geom_errorbar(width=.25, aes(ymin=prop-ci, ymax=prop+ci)) +
  facet_grid(. ~ condition ) +
  xlab("PAS") + 
  ylab("proportion") +
  ggtitle("proportion of each PAS (third presentation) in each condition")

```


looking at first presentations

```{r,echo=FALSE,warning=FALSE}
ggplot(dfwc1, aes(x=studyResp, y=named)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  geom_errorbar(width=.25, aes(ymin=named-ci, ymax=named+ci)) +
  facet_grid(. ~ condition ) +
  xlab("PAS") + 
  ylab("named") +
  ggtitle("% named for each condition, given first PAS")

```

```{r,echo=FALSE,warning=FALSE}
ggplot(dfwc1, aes(x=studyResp, y=prop)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  geom_errorbar(width=.25, aes(ymin=prop-ci, ymax=prop+ci)) +
  facet_grid(. ~ condition ) +
  xlab("PAS") + 
  ylab("proportion") +
  ggtitle("proportion of each PAS (first presentation) in each condition")

```


```{r, pas_conditional,echo=FALSE,warning=FALSE}
dfwc_pas <- summarySEwithin(data, measurevar="named", withinvars=c("studyResp","studyResp3"),
                            idvar="subject", na.rm=FALSE, conf.interval=.95)

dfwc_pas<-ddply(dfwc_pas,.(studyResp3),transform,p3Gp1=N/sum(N))

dfwc_pas_cfs <- summarySEwithin(data[data$condition==3,], measurevar="named",                          withinvars=c("studyResp","studyResp3"),
                                idvar="subject", na.rm=FALSE, conf.interval=.95)

dfwc_pas_cfs<-ddply(dfwc_pas_cfs,.(studyResp3),transform,p3Gp1=N/sum(N))




```


```{r,pas_condi_graph,echo=FALSE,warning=FALSE}

ggplot(dfwc_pas, aes(x=studyResp3, y=p3Gp1)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  facet_grid(. ~ studyResp ) +
  facet_wrap(~ studyResp, ncol=3) +
  xlab("PAS") + 
  ylab("p(PAS_3|PAS_1)") +
  ggtitle(" Proportion of thrid PAS given first PAS ")


```

NOTE: the above graph is somewhat confounded by condition. the following graph is looking only at study responses to the cfs condition



```{r,pas_condi_,echo=FALSE,warning=FALSE}

ggplot(dfwc_pas_cfs, aes(x=studyResp3, y=p3Gp1)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  facet_grid(. ~ studyResp ) +
  facet_wrap(~ studyResp, ncol=3) +
  xlab("PAS") + 
  ylab("p(PAS_3|PAS_1)") +
  ggtitle(" Proportion of thrid PAS given first PAS ")


```


now, scatter plots



```{r,stateTrace_avg,warning=FALSE,echo=FALSE}
afc_all <- summarySEwithin(data, measurevar="afc",
                           withinvars=c("condition"),
                           idvar="subject", na.rm=TRUE, conf.interval=.95)

name_all <- summarySEwithin(data, measurevar="named",
                            withinvars=c("condition"),
                            idvar="subject", na.rm=TRUE, conf.interval=.95)


toPlot_stAll <- cbind(named=name_all$named
                      ,named_norm=name_all$named_norm
                      ,ci_named=name_all$ci
                      ,afc_all
                      ,count=(afc_all$N+name_all$N)/2)

```


```{r,st_plot_avg,warning=FALSE,echo=FALSE}
pd <- position_dodge(0.001)

ggplot(toPlot_stAll, aes(x=afc_norm, y=named_norm, colour=condition, group=condition)) +
  geom_errorbar(aes(ymin=named_norm-ci_named, ymax=named_norm+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc_norm-ci, xmax=afc_norm+ci), colour="black", height = .05, position=pd) +
  ylim(0,1) +
  xlim(0,1) +
  geom_point(position=pd, size=1)  +  #aes(size=count)
  ggtitle("state trace, for each condition, collapsed across PAS") +
  theme(aspect.ratio = 1) +
  theme(axis.ticks = element_blank(), axis.text.x = element_blank()) +
  theme(axis.ticks = element_blank(), axis.text.y = element_blank())



```

```{r,echo=FALSE,warning=FALSE}
# state trace plots


dfwc3_afc <- summarySEwithin(data, measurevar="afc"                       , withinvars=c("condition","studyResp3"),
                             idvar="subject", na.rm=TRUE, conf.interval=.95)

toPlot3 <- cbind(named=dfwc3$named,ci_named=dfwc3$ci
                 ,dfwc3_afc,count=(dfwc3$N+dfwc3_afc$N)/2)


dfwc1_afc <- summarySEwithin(data, measurevar="afc"                       , withinvars=c("condition","studyResp"),
                             idvar="subject", na.rm=TRUE, conf.interval=.95)

toPlot1 <- cbind(named=dfwc1$named,ci_named=dfwc1$ci
                 ,dfwc1_afc,count=(dfwc1$N+dfwc1_afc$N)/2)

```


```{r,scatterPlots_third_noSize,echo=FALSE,warning=FALSE}

ggplot(toPlot3, aes(x=afc, y=named, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
  ylim(0,1) +
  xlim(0,1) +
  geom_point(position=pd, size=1) +
  facet_grid(. ~ studyResp3 ) +
  facet_wrap(~ studyResp3, ncol=3) +
  ggtitle("state trace, facets indicate PAS response on third presentation (1e+05 => foil)") +
  theme(aspect.ratio = 1) 



```





```{r,scatterPlots_third,echo=FALSE,warning=FALSE}
pd <- position_dodge(0.001)

ggplot(toPlot3, aes(x=afc, y=named, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
  ylim(0,1) +
  xlim(0,1) +
  geom_point(position=pd, aes(size=count)) +
  scale_size_continuous(breaks=c(10,100,200,400,600)) +
  facet_grid(. ~ studyResp3 ) +
  facet_wrap(~ studyResp3, ncol=3) +
  ggtitle("state trace, facets indicate PAS response on third presentation (1e+05 => foil)") +
  theme(aspect.ratio = 1) 



```


In the above graph, size of dot indicates amount of data going in to point

```{r,scatterPlots_first,echo=FALSE,warning=FALSE}
pd <- position_dodge(0.001)

ggplot(toPlot1, aes(x=afc, y=named, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
  ylim(0,1) +
  xlim(0,1) +
  geom_point(position=pd, aes(size=count))  +
  scale_size_continuous(breaks=c(10,100,200,400,600)) +
  facet_grid(. ~ studyResp ) +
  facet_wrap(~ studyResp, ncol=3) +
  ggtitle("state trace, facets indicate PAS response on first presentation (1e+05 => foil)") +
  theme(aspect.ratio = 1)


```


now, look at individual subjects (normalized scores)

```{r,subData,echo=FALSE,warning=FALSE}
afc_sub <- summarySEwithin(data, measurevar="afc",
                           withinvars=c("condition","subject"),
                           idvar="subject", na.rm=TRUE, conf.interval=.95)

name_sub <- summarySEwithin(data, measurevar="named",
                            withinvars=c("condition","subject"),
                            idvar="subject", na.rm=TRUE, conf.interval=.95)


toPlot_sub <- cbind(named=name_sub$named
                    ,named_norm=name_sub$named_norm
                    ,ci_named=name_sub$ci
                    ,afc_sub
                    ,count=(afc_sub$N+name_sub$N)/2)



```


```{r,st_sub_graph1,echo=FALSE,warning=FALSE}
pd <- position_dodge(0.001)

ggplot(toPlot_sub, aes(x=afc_norm, y=named_norm, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named_norm-ci_named, ymax=named_norm+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc_norm-ci, xmax=afc_norm+ci), colour="black", height = .05, position=pd) +
  ylim(0,1) +
  xlim(0,1) +
  geom_point(position=pd, size=1)  +  #aes(size=count)
  #  scale_size_continuous(breaks=c(10,100,200,400,600)) +
  facet_grid(. ~ subject ) +
  facet_wrap(~ subject, ncol=8) +
  ggtitle("state trace, by subject, normalized scores") +
  theme(aspect.ratio = 1) +
  theme(axis.ticks = element_blank(), axis.text.x = element_blank()) +
  theme(axis.ticks = element_blank(), axis.text.y = element_blank())


```


```{r,st_sub_graph2,echo=FALSE,warning=FALSE}
pd <- position_dodge(0.001)

ggplot(toPlot_sub, aes(x=afc, y=named, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
  ylim(0,1) +
  xlim(0,1) +
  geom_point(position=pd, size=1)  +  #aes(size=count)
  #  scale_size_continuous(breaks=c(10,100,200,400,600)) +
  facet_grid(. ~ subject ) +
  facet_wrap(~ subject, ncol=8) +
  ggtitle("state trace, by subject, raw scores") +
  theme(aspect.ratio = 1) +
  theme(axis.ticks = element_blank(), axis.text.x = element_blank()) +
  theme(axis.ticks = element_blank(), axis.text.y = element_blank())


```
