---
title: "CFS, 2AFC, Short Study Lists"
author: "pss"
date: "February 10, 2016"
output: pdf_document
---

summary of results for cfs study

Version: presentation in lists of 16. Items studied x3 times 
  Note that second/third presentation was in the same order as first presentations
  all items studied for total of .5 seconds (including ramping up and down)



```{r,echo=FALSE}
# preamble


library(ggplot2)
library(plyr)


error.bar <- function(x, y, upper, lower=upper, length=0.1,...){
  if(length(x) != length(y) | length(y) !=length(lower) | length(lower) != length(upper))
    stop("vectors must be same length")
  arrows(x,y+upper, x, y-lower, angle=90, code=3, length=length, ...)
}


# preliminary changing of folders
#setwd("D:/googleDrive/uMass/firstYear/behavioralExpts/pSadil/processDissociation/CFS/analysisCode/R/afc/shortStudyLists")

wd <- getwd()

dataFile <- paste(wd, "/cfs_obj_2afc_ss1.dat", sep="")
# find the data that was generated from the matlab files
data <- read.csv(dataFile)

# add 1 to study resp because participants were instructed to use 0-3
data$studyResp = data$studyResp+1
data$studyResp2 = data$studyResp2+1
data$studyResp3 = data$studyResp3+1

nConds = max(data$condition,na.rm=TRUE)
nPAS = max(data[data$studyResp < 1000,]$studyResp,na.rm=TRUE)
nItems = max(data$whichItem,na.rm=TRUE)
nSubs = max(data$subject,na.rm=TRUE)
nTrials = max(data$trial,na.rm=TRUE)
nInCond = nItems / nConds

# number of items in each condition, first presentation
nPerCond = nItems/nConds


data$trial = as.factor(data$trial)
data$whichItem = as.factor(data$whichItem)
data$subject = as.factor(data$subject)
data$condition = as.factor(data$condition)
#data$condition = as.numeric(data$condition)
# don't want PAS as a factor, because there are 
# vastly different numbers of each kind of response
# Do I want condition as factor? if it were, that would
# seem to make stronger claims (justified) about higher levels
# leading to higher recall rates
studyConds <- c("foil","word","cfs","binoc")
cols <- c('black', 'cornflowerblue', 'darkgoldenrod1', 'red')
pasResps <- c("0","1","2","3")

# trim away missing values (there aren't, currently)
data_trim <- na.omit(data)


```


```{r}
cutoff = 3 # only look at CFS with PAS 2 or 1
nPresent = 3 # presented 3 times
nStudy = nTrials * nPresent

```

```{r, echo=FALSE}
rRates.pasCond_mean = array(0,dim=c(nConds,nPAS,nPresent))
rRates.pasCond_sem = array(0,dim=c(nConds,nPAS,nPresent))
rRates.pasCond_n = array(0,dim=c(nConds,nPAS,nPresent))
for (cond in 1:nConds) {
  for (pas in 1:nPAS) {
    
    rRates.pasCond_mean[cond,pas,1] <- 
      mean(data_trim[data_trim$condition==cond &
                       data_trim$studyResp==pas,]$named,
           na.rm=TRUE)
    
    rRates.pasCond_n[cond,pas,1] <- 
      dim(data_trim[data_trim$condition==cond & 
                      data_trim$studyResp==pas,])[1]
    
    # var = n*p*(1-p)
    rRates.pasCond_sem[cond,pas,1] <-
      sqrt(rRates.pasCond_n[cond,pas,1] * rRates.pasCond_mean[cond,pas,1] * 
             (1- rRates.pasCond_mean[cond,pas,1])) / 
      sqrt(rRates.pasCond_n[cond,pas,1])
    
    
    # second presentation
    rRates.pasCond_mean[cond,pas,2] <- 
      mean(data_trim[data_trim$condition==cond &
                       data_trim$studyResp2==pas,]$named,
           na.rm=TRUE)
    
    rRates.pasCond_n[cond,pas,2] <- 
      dim(data_trim[data_trim$condition==cond & 
                      data_trim$studyResp2==pas,])[1]
    
    rRates.pasCond_sem[cond,pas,2] <-
      sqrt(rRates.pasCond_n[cond,pas,2] * rRates.pasCond_mean[cond,pas,2] * 
             (1- rRates.pasCond_mean[cond,pas,2])) / 
      sqrt(rRates.pasCond_n[cond,pas,2])
    
    # third presentation
    rRates.pasCond_mean[cond,pas,3] <- 
      mean(data_trim[data_trim$condition==cond &
                       data_trim$studyResp3==pas,]$named,
           na.rm=TRUE)
    
    rRates.pasCond_n[cond,pas,3] <- 
      dim(data_trim[data_trim$condition==cond & 
                      data_trim$studyResp3==pas,])[1]
    
    rRates.pasCond_sem[cond,pas,3] <-
      sqrt(rRates.pasCond_n[cond,pas,3] * rRates.pasCond_mean[cond,pas,3] * 
             (1- rRates.pasCond_mean[cond,pas,3])) / 
      sqrt(rRates.pasCond_n[cond,pas,3])
    
    
  }
}

rRates.pasCond_n.prop = array(0,dim=c(nConds,nPAS,nPresent))
for (cond in 1:nConds) {
  for (pas in 1:nPAS){
    rRates.pasCond_n.prop[cond,pas,1] <- 
      rRates.pasCond_n[cond,pas,1] / 
      sum(rRates.pasCond_n[cond,,1])
    
    # second presentation
    rRates.pasCond_n.prop[cond,pas,2] <- 
      rRates.pasCond_n[cond,pas,2] / 
      sum(rRates.pasCond_n[cond,,2])
    
    # third presentation
    rRates.pasCond_n.prop[cond,pas,3] <- 
      rRates.pasCond_n[cond,pas,3] / 
      sum(rRates.pasCond_n[cond,,3])
    
    
  }
}



```
 
 
The following is a graph of the proportion of times that an item was named,
conditioned on a given PAS response.

Note that eror bars are weird because they're just simple SEMs. Currently unclear about the best ways to make error bars for variables bounded between 1 and 0.

Additionally, it is somewhat misleading to include error bars across a within-subjects factor. They could be higher than depicted, and do not accurately reflect whatever statistics will eventually be performed.

```{r,echo=FALSE,warning=FALSE}
par(mfrow=c(1,1))
pasCond.bp <- barplot(t(rRates.pasCond_mean[,,1]),
                  beside=TRUE,
                  names.arg=studyConds,
                  ylim=c(0,1),
                  #col=presentCol,
                  legend.text=pasResps,
                  args.legend = list(x="topleft"),
                  xlab = "study length",
                  ylab = "proportion named"
                  , main = "first presentation"
                  
)
error.bar(pasCond.bp,t(rRates.pasCond_mean[,,1]),
          t(rRates.pasCond_sem[,,1]))



par(mfrow=c(1,1))
pasResps <- c("0","1","2","3")
pasCond.bp <- barplot(t(rRates.pasCond_mean[,,2]),
                  beside=TRUE,
                  names.arg=studyConds,
                  ylim=c(0,1),
                  #col=presentCol,
                  legend.text=pasResps,
                  args.legend = list(x="topleft"),
                  xlab = "study length",
                  ylab = "proportion named"
                  , main = "second presentation"
                  
)
error.bar(pasCond.bp,t(rRates.pasCond_mean[,,2]),
          t(rRates.pasCond_sem[,,2]))

par(mfrow=c(1,1))
pasResps <- c("0","1","2","3")
pasCond.bp <- barplot(t(rRates.pasCond_mean[,,3]),
                  beside=TRUE,
                  names.arg=studyConds,
                  ylim=c(0,1),
                  #col=presentCol,
                  legend.text=pasResps,
                  args.legend = list(x="topleft"),
                  xlab = "study length",
                  ylab = "proportion named"
                  , main = "third presentation"
                  
)
error.bar(pasCond.bp,t(rRates.pasCond_mean[,,3]),
          t(rRates.pasCond_sem[,,3]))

```


Next up is a plot of the proportion of times that an item was given a particular 
PAS rating

```{r,echo=FALSE}

par(mfrow=c(1,1))
# looking at raw numbers of each PAS per condition
pasCond_n.bp <- barplot(t(rRates.pasCond_n.prop[,,1]),
                        beside=TRUE,
                        names.arg=studyConds,
                        ylim=c(0,1),
                        #col=presentCol,
                        legend.text=pasResps,
                        args.legend = list(x="topleft"),
                        xlab = "study length",
                        ylab = "proportion of responses"
                        , main  = 'first presentation'
)


par(mfrow=c(1,1))
# looking at raw numbers of each PAS per condition
pasCond_n.bp <- barplot(t(rRates.pasCond_n.prop[,,2]),
                        beside=TRUE,
                        names.arg=studyConds,
                        ylim=c(0,1),
                        #col=presentCol,
                        legend.text=pasResps,
                        args.legend = list(x="topleft"),
                        xlab = "study length",
                        ylab = "proportion of resposnes"
                        , main = "second presentation"
)


par(mfrow=c(1,1))
# looking at raw numbers of each PAS per condition
pasCond_n.bp <- barplot(t(rRates.pasCond_n.prop[,,3]),
                        beside=TRUE,
                        names.arg=studyConds,
                        ylim=c(0,1),
                        #col=presentCol,
                        legend.text=pasResps,
                        args.legend = list(x="topleft"),
                        xlab = "study length",
                        ylab = "proportion of resposnes"
                        , main = "third presentation"
)

```

now, scatter plots

```{r,echo=FALSE}
# look at recal rates for pas < cutoff, collapsed across subs
rRates.cond_mean = matrix(0,nrow=nConds,ncol=nPresent)
rRates.cond_sem = matrix(0,nrow=nConds,ncol=nPresent)
rRates.cond_n = matrix(0,nrow=nConds,ncol=nPresent)
for (cond in 1:nConds) {
  
  if (cond == 3){
    rRates.cond_mean[cond,1] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp == 3 ),]$named,
           na.rm=TRUE)
    
    rRates.cond_n[cond,1] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp == 3 ),])[1]
    
    rRates.cond_mean[cond,2] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp2 == 3),]$named,
           na.rm=TRUE)
    
    rRates.cond_n[cond,2] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp2 == 3 ),])[1]

    
    # third presentation
        rRates.cond_mean[cond,3] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp3 == 3),]$named,
           na.rm=TRUE)
    
    rRates.cond_n[cond,3] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp3 == 3 ),])[1]

        
  } else {
    rRates.cond_mean[cond,] <- 
      mean(data_trim[data_trim$condition==cond,]$named,
           na.rm=TRUE)
    
    rRates.cond_n[cond,] <- 
      dim(data_trim[data_trim$condition==cond,])[1]
  }
  
  # var = n*p*(1-p)
  rRates.cond_sem[cond,] <-
    sqrt(rRates.cond_n[cond,] * rRates.cond_mean[cond,] * 
           (1- rRates.cond_mean[cond,])) / 
    sqrt(rRates.cond_n[cond,])
  
}

# look at 2afc rates for pas < 3, collapsed across subs
afcRates.cond_mean = matrix(0,nrow=nConds,ncol=nPresent)
afcRates.cond_sem = matrix(0,nrow=nConds,ncol=nPresent)
afcRates.cond_n = matrix(0,nrow=nConds,ncol=nPresent)
for (cond in 1:nConds) {
  
  if (cond == 3){
    afcRates.cond_mean[cond,1] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp == 3),]$afc,
           na.rm=TRUE)
    
    afcRates.cond_n[cond,1] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp == 3 ),])[1]
    
    # second presentation
    afcRates.cond_mean[cond,2] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp2 == 3),]$afc,
           na.rm=TRUE)
    
    afcRates.cond_n[cond,2] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp2 == 3 ),])[1]

        # third presentation
    afcRates.cond_mean[cond,3] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp3 == 3),]$afc,
           na.rm=TRUE)
    
    afcRates.cond_n[cond,3] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp3 == 3 ),])[1]

    
        
  } else {
    afcRates.cond_mean[cond,] <- 
      mean(data_trim[data_trim$condition==cond,]$afc,
           na.rm=TRUE)
    
    afcRates.cond_n[cond,] <- 
      dim(data_trim[data_trim$condition==cond,])[1]
  }
  
  # var = n*p*(1-p)
  afcRates.cond_sem[cond,] <-
    sqrt(afcRates.cond_n[cond,] * afcRates.cond_mean[cond,] * 
           (1- rRates.cond_mean[cond,])) / 
    sqrt(afcRates.cond_n[cond,])
  
}

```


```{r,echo=FALSE}
# code for state trace plots

# par(mfrow=c(1,1))
# new <- plot(afcRates.cond_mean[,1],rRates.cond_mean[,1]
#             , xlim = c(0,1)
#             , ylim = c(0,1)
#             , col = cols
#             , xlab = 'prop 2afc correct'
#             , ylab = 'recall rate'
#             , main = 'PAS < cutoff (firstPresent), subs > 50% respond'
# )
# legend("topleft", legend = studyConds,
#        col=cols,pch = 1,bty="n")


# par(mfrow=c(1,1))
# new <- plot(afcRates.cond_mean[,2],rRates.cond_mean[,2]
#      , xlim = c(0,1)
#      , ylim = c(0,1)
#      , col = cols
#      , xlab = 'prop 2afc correct'
#      , ylab = 'recall rate'
#      , main = 'PAS < cutoff (secondPresent), subs > 50% respond'
# )
# legend("topleft", legend = studyConds,
#        col=cols,pch = 1,bty="n")
# 
# 
# par(mfrow=c(1,1))
# new <- plot(afcRates.cond_mean[,3],rRates.cond_mean[,3]
#      , xlim = c(0,1)
#      , ylim = c(0,1)
#      , col = cols
#      , xlab = 'prop 2afc correct'
#      , ylab = 'recall rate'
#      , main = 'PAS < cutoff (thirdPresent), subs > 50% respond'
# )
# legend("topleft", legend = studyConds,
#        col=cols,pch = 1,bty="n")


```


CFS performance is conditioned on having responded 0-2 at the third study opportunity.
Binocular and Word is conditioned on having responded 3


```{r, echo=FALSE}

par(mfrow=c(1,1))
# plot first point (to initilize graph)
plot(  x = mean(data_trim[data_trim$condition==1,]$afc, na.rm=TRUE)
       , y = mean(data_trim[data_trim$condition==1,]$named, na.rm=TRUE)
       , xlim = c(0,1)
       , ylim = c(0,1)
       , col = cols[1]
       , xlab = 'prop 2afc correct'
       , ylab = 'recall rate'
       , main = ' '
)

# plot remaining points of non-cfs conditions
for (cond in c(2,4)){
  points(  x = mean(data_trim[data_trim$condition==cond
                              & data_trim$studyResp3==4
                              ,]$afc, na.rm=TRUE)
           , y = mean(data_trim[data_trim$condition==cond
                                & data_trim$studyResp3==4
                                ,]$named, na.rm=TRUE)
           , col = cols[cond]
           , pch = 1
  )
}
  
for (resp in 1:4) {
  points(  x = mean(data_trim[data_trim$condition==3 & data_trim$studyResp3==resp
                              ,]$afc, na.rm=TRUE)
           , y = mean(data_trim[data_trim$condition==3 & data_trim$studyResp3==resp
                                ,]$named, na.rm=TRUE)
           , col = cols[3]
           , pch = resp+1
  )
}

legend("left", legend = 
         c(studyConds[1],rep(studyConds[c(2,4)],each=1),rep(studyConds[3],4))
       ,col=c(cols[1],rep(cols[c(2,4)],each=1),rep(cols[3],4))
       ,pch = c(rep(1,3),2:5),bty="n")


```


comparing PAS responses for words and binocular. Note, many possible points are missing. Those correspond to cases that never occurred, like a rating of 1 to the binocular condition

```{r, echo=FALSE}

par(mfrow=c(1,1),mar=c(1,1,1,1)+0.1)
# plot first point (to initilize graph)
plot(  x = mean(data_trim[data_trim$condition==1,]$afc, na.rm=TRUE)
       , y = mean(data_trim[data_trim$condition==1,]$named, na.rm=TRUE)
       , xlim = c(0,1)
       , ylim = c(0,1)
       , col = cols[1]
       , xlab = 'prop 2afc correct'
       , ylab = 'recall rate'
       , main = ' '
)

# plot remaining points of non-cfs conditions
for (cond in c(2,4)){
  for (resp in 1:4){
    points(  x = mean(data_trim[data_trim$condition==cond
                                & data_trim$studyResp3==resp
                                ,]$afc, na.rm=TRUE)
             , y = mean(data_trim[data_trim$condition==cond
                                  & data_trim$studyResp3==resp
                                  ,]$named, na.rm=TRUE)
             , col = cols[cond]
             , pch = resp+1
    )
  }
}
  
for (resp in 1:4) {
  points(  x = mean(data_trim[data_trim$condition==3 & data_trim$studyResp3==resp
                              ,]$afc, na.rm=TRUE)
           , y = mean(data_trim[data_trim$condition==3 & data_trim$studyResp3==resp
                                ,]$named, na.rm=TRUE)
           , col = cols[3]
           , pch = resp+1
  )
}

legend("left", legend = 
         c(studyConds[1],rep(studyConds[c(2,4)],each=4),rep(studyConds[3],4))
       ,col=c(cols[1],rep(cols[c(2,4)],each=4),rep(cols[3],4))
       ,pch = c(1,rep(2:5,times=3)),bty="n")


```








Plot just the average of CFS, given responses below 3

```{r, echo=FALSE}

par(mfrow=c(1,1))
# plot first point (to initilize graph)
plot(  x = mean(data_trim[data_trim$condition==1,]$afc, na.rm=TRUE)
       , y = mean(data_trim[data_trim$condition==1,]$named, na.rm=TRUE)
       , xlim = c(0,1)
       , ylim = c(0,1)
       , col = cols[1]
       , xlab = 'prop 2afc correct'
       , ylab = 'recall rate'
       , main = ' '
)

# plot remaining points of non-cfs conditions
for (cond in c(2,4)){
  points(  x = mean(data_trim[data_trim$condition==cond,]$afc, na.rm=TRUE)
                , y = mean(data_trim[data_trim$condition==cond,]$named, na.rm=TRUE)
                , col = cols[cond]
  )
}

points(  x = mean(data_trim[data_trim$condition==3 
                            & (data_trim$studyResp3==1 | data_trim$studyResp3==2 | data_trim$studyResp3==3) 
                            ,]$afc, na.rm=TRUE)
         , y = mean(data_trim[data_trim$condition==3 
                              & (data_trim$studyResp3==1 | data_trim$studyResp3==2 | data_trim$studyResp3==3) 
                              ,]$named, na.rm=TRUE)
         , col = cols[3]
         , pch = 1
)

legend("topleft", legend = c(studyConds[1:2],studyConds[4],rep(studyConds[3],1)),
       col=c(cols[1:2],cols[4],cols[3]),pch = c(rep(1,times=3),2),bty="n")


```




By Subjects

Still looking at test performance as judged by third PAS response

```{r, echo=FALSE}
par(mfrow=c(2,4))
for (sub in 1:8) {
  # plot first point (to initilize graph)
  plot(  x = mean(data_trim[data_trim$condition==1 
                            & data_trim$subject==sub
                            ,]$afc, na.rm=TRUE)
         , y = mean(data_trim[data_trim$condition==1
                              & data_trim$subject==sub
                              ,]$named, na.rm=TRUE)
         , xlim = c(0,1)
         , ylim = c(0,1)
         , col = cols[1]
         , xlab = 'prop 2afc correct'
         , ylab = 'recall rate'
         , main = c('sub', as.character(sub))
  )
  
  # plot remaining points of non-cfs conditions
  for (cond in c(2,4)){
    points(  x = mean(data_trim[data_trim$condition==cond
                                & data_trim$subject==sub
                                ,]$afc, na.rm=TRUE)
             , y = mean(data_trim[data_trim$condition==cond
                                  & data_trim$subject==sub
                                  ,]$named, na.rm=TRUE)
             , col = cols[cond]
    )
  }
  
  for (resp in unique(data_trim$studyResp)) {
    points(  x = mean(data_trim[data_trim$condition==3 
                                & data_trim$studyResp3==resp
                                & data_trim$subject==sub
                                ,]$afc, na.rm=TRUE)
             , y = mean(data_trim[data_trim$condition==3 
                                  & data_trim$studyResp3==resp
                                  & data_trim$subject==sub
                                  ,]$named, na.rm=TRUE)
             , col = cols[3]
             , pch = resp+1
    )
  }
  
#   legend("topleft", legend = c(studyConds[1:2],studyConds[4],rep(studyConds[3],4)),
#          col=c(cols[1:2],cols[4],rep(cols[3],4)),pch = c(rep(1,times=3),2:5),bty="n")
  
}
```


```{r,echo=FALSE}
par(mfrow=c(2,4))

for (sub in 9:16) {
  # plot first point (to initilize graph)
  plot(  x = mean(data_trim[data_trim$condition==1 
                            & data_trim$subject==sub
                            ,]$afc, na.rm=TRUE)
         , y = mean(data_trim[data_trim$condition==1
                              & data_trim$subject==sub
                              ,]$named, na.rm=TRUE)
         , xlim = c(0,1)
         , ylim = c(0,1)
         , col = cols[1]
         , xlab = 'prop 2afc correct'
         , ylab = 'recall rate'
         , main = c('sub', as.character(sub))
  )
  
  # plot remaining points of non-cfs conditions
  for (cond in c(2,4)){
    points(  x = mean(data_trim[data_trim$condition==cond
                                & data_trim$subject==sub
                                ,]$afc, na.rm=TRUE)
             , y = mean(data_trim[data_trim$condition==cond
                                  & data_trim$subject==sub
                                  ,]$named, na.rm=TRUE)
             , col = cols[cond]
    )
  }
  
  for (resp in unique(data_trim$studyResp)) {
    points(  x = mean(data_trim[data_trim$condition==3 
                                & data_trim$studyResp3==resp
                                & data_trim$subject==sub
                                ,]$afc, na.rm=TRUE)
             , y = mean(data_trim[data_trim$condition==3 
                                  & data_trim$studyResp3==resp
                                  & data_trim$subject==sub
                                  ,]$named, na.rm=TRUE)
             , col = cols[3]
             , pch = resp+1
    )
  }
  
#   legend("topleft", legend = c(studyConds[1:2],studyConds[4],rep(studyConds[3],4)),
#          col=c(cols[1:2],cols[4],rep(cols[3],4)),pch = c(rep(1,times=3),2:5),bty="n")
  
}
```






```{r}
# rRates.cond_sem
# afcRates.cond_sem

```

next, look at the state traces by subject

```{r,echo=FALSE}
# rRates_sub.cond_mean = array(0,dim=c(nConds,nSubs,nPresent))
# rRates_sub.cond_sem = array(0,dim=c(nConds,nSubs,nPresent))
# rRates_sub.cond_n = array(0,dim=c(nConds,nSubs,nPresent))
# for (cond in 1:nConds) {
#   for (sub in 1:nSubs){
#     
#     if (cond == 3){
#       rRates_sub.cond_mean[cond,sub,1] <- 
#         mean(data_trim[data_trim$condition==cond &
#                          (data_trim$studyResp < cutoff)
#                           & data_trim$subject==sub,]$named,
#              na.rm=TRUE)
#       
#       rRates_sub.cond_n[cond,sub,1] <- 
#         dim(data_trim[data_trim$condition==cond & 
#                         (data_trim$studyResp < cutoff)
#                          & data_trim$subject==sub,])[1]
#       
#       # second presentation
#       rRates_sub.cond_mean[cond,sub,2] <- 
#         mean(data_trim[data_trim$condition==cond &
#                          (data_trim$studyResp2 < cutoff)
#                        & data_trim$subject==sub,]$named,
#              na.rm=TRUE)
#       
#       rRates_sub.cond_n[cond,sub,2] <- 
#         dim(data_trim[data_trim$condition==cond & 
#                         (data_trim$studyResp2 < cutoff)
#                       & data_trim$subject==sub,])[1]
#       
#       
#             # third presentation
#       rRates_sub.cond_mean[cond,sub,3] <- 
#         mean(data_trim[data_trim$condition==cond &
#                          (data_trim$studyResp3 < cutoff)
#                        & data_trim$subject==sub,]$named,
#              na.rm=TRUE)
#       
#       rRates_sub.cond_n[cond,sub,3] <- 
#         dim(data_trim[data_trim$condition==cond & 
#                         (data_trim$studyResp3 < cutoff)
#                       & data_trim$subject==sub,])[1]
# 
#       
#     } else {
#       rRates_sub.cond_mean[cond,sub,] <- 
#         mean(data_trim[data_trim$condition==cond
#                        & data_trim$subject==sub,]$named,
#              na.rm=TRUE)
#       
#       rRates_sub.cond_n[cond,sub,] <- 
#         dim(data_trim[data_trim$condition==cond
#                       & data_trim$subject==sub,])[1]
#     }
#     
#     # var = n*p*(1-p)
#     rRates_sub.cond_sem[cond,sub,1] <-
#       sqrt(rRates_sub.cond_n[cond,sub,1] * rRates_sub.cond_mean[cond,sub,1] * 
#              (1- rRates_sub.cond_mean[cond,sub,1])) / 
#       sqrt(rRates_sub.cond_n[cond,sub,1])
#     
#     # second present
#     rRates_sub.cond_sem[cond,sub,2] <-
#       sqrt(rRates_sub.cond_n[cond,sub,2] * rRates_sub.cond_mean[cond,sub,2] * 
#              (1- rRates_sub.cond_mean[cond,sub,2])) / 
#       sqrt(rRates_sub.cond_n[cond,sub,2])
#     
#         # third present
#     rRates_sub.cond_sem[cond,sub,3] <-
#       sqrt(rRates_sub.cond_n[cond,sub,3] * rRates_sub.cond_mean[cond,sub,3] * 
#              (1- rRates_sub.cond_mean[cond,sub,3])) / 
#       sqrt(rRates_sub.cond_n[cond,sub,3])
#   }
# }
# 
# # look at 2afc rates for pas < 3, collapsed across subs
# afcRates_sub.cond_mean = array(0,dim=c(nConds,nSubs,nPresent))
# afcRates_sub.cond_sem = array(0,dim=c(nConds,nSubs,nPresent))
# afcRates_sub.cond_n = array(0,dim=c(nConds,nSubs,nPresent))
# for (cond in 1:nConds) {
#   for(sub in 1:nSubs){
#     if (cond == 3){
#       afcRates_sub.cond_mean[cond,sub,1] <- 
#         mean(data_trim[data_trim$condition==cond &
#                          (data_trim$studyResp < cutoff)
#                        & data_trim$subject==sub,]$afc,
#              na.rm=TRUE)
#       
#       afcRates_sub.cond_n[cond,sub,1] <- 
#         dim(data_trim[data_trim$condition==cond & 
#                         (data_trim$studyResp < cutoff )
#                       & data_trim$subject==sub,])[1]
#       
#       # second present
#       afcRates_sub.cond_mean[cond,sub,2] <- 
#         mean(data_trim[data_trim$condition==cond &
#                          (data_trim$studyResp2 < cutoff)
#                        & data_trim$subject==sub,]$afc,
#              na.rm=TRUE)
#       
#       afcRates_sub.cond_n[cond,sub,2] <- 
#         dim(data_trim[data_trim$condition==cond & 
#                         (data_trim$studyResp2 < cutoff )
#                       & data_trim$subject==sub,])[1]
# 
#             # third present
#       afcRates_sub.cond_mean[cond,sub,3] <- 
#         mean(data_trim[data_trim$condition==cond &
#                          (data_trim$studyResp3 < cutoff)
#                        & data_trim$subject==sub,]$afc,
#              na.rm=TRUE)
#       
#       afcRates_sub.cond_n[cond,sub,3] <- 
#         dim(data_trim[data_trim$condition==cond & 
#                         (data_trim$studyResp3 < cutoff )
#                       & data_trim$subject==sub,])[1]
# 
#       
#             
#     } else {
#       afcRates_sub.cond_mean[cond,sub,] <- 
#         mean(data_trim[data_trim$condition==cond
#                        & data_trim$subject==sub,]$afc,
#              na.rm=TRUE)
#       
#       afcRates_sub.cond_n[cond,sub,] <- 
#         dim(data_trim[data_trim$condition==cond
#                       & data_trim$subject==sub,])[1]
#     }
#     
#     # var = n*p*(1-p)
#     afcRates_sub.cond_sem[cond,sub,1] <-
#       sqrt(afcRates_sub.cond_n[cond,sub,1] * afcRates_sub.cond_mean[cond,sub,1] * 
#              (1- rRates_sub.cond_mean[cond,sub,1])) / 
#       sqrt(afcRates_sub.cond_n[cond,sub,1])
#     
#     # second present
#     afcRates_sub.cond_sem[cond,sub,2] <-
#       sqrt(afcRates_sub.cond_n[cond,sub,2] * afcRates_sub.cond_mean[cond,sub,2] * 
#              (1- rRates_sub.cond_mean[cond,sub,2])) / 
#       sqrt(afcRates_sub.cond_n[cond,sub,2])
#     
#         # third present
#     afcRates_sub.cond_sem[cond,sub,3] <-
#       sqrt(afcRates_sub.cond_n[cond,sub,3] * afcRates_sub.cond_mean[cond,sub,3] * 
#              (1- rRates_sub.cond_mean[cond,sub,3])) / 
#       sqrt(afcRates_sub.cond_n[cond,sub,3])
# 
#     
#   }
# }

```


**first presentation**

```{r,echo=FALSE}
# # code for plots
# 
# par(mfrow=c(2,4))
# for (sub in 1:nSubs){
#   
#   plot(afcRates_sub.cond_mean[,sub,1],rRates_sub.cond_mean[,sub,1]
#        , xlim = c(0,1)
#        , ylim = c(0,1)
#        , col = cols
#        , xlab = 'prop 2afc correct'
#        , ylab = 'recall rate'
#        , main = c('sub', as.character(sub))
#   )
#   #legend("topleft", legend = studyConds,
#    #      col=cols,pch = 1,bty="n")
#   
# }

```

**second presentation**

```{r,echo=FALSE}
# # code for plots
# 
# par(mfrow=c(2,4))
# for (sub in 1:nSubs){
#   
#   plot(afcRates_sub.cond_mean[,sub,2],rRates_sub.cond_mean[,sub,2]
#        , xlim = c(0,1)
#        , ylim = c(0,1)
#        , col = cols
#        , xlab = 'prop 2afc correct'
#        , ylab = 'recall rate'
#        , main = c('sub', as.character(sub))
#   )
#   #legend("topleft", legend = studyConds,
#    #      col=cols,pch = 1,bty="n")
#   
# }

```

**third presentation**

```{r,echo=FALSE}
# # code for plots
# 
# par(mfrow=c(2,4))
# for (sub in 1:nSubs){
#   
#   plot(afcRates_sub.cond_mean[,sub,3],rRates_sub.cond_mean[,sub,3]
#        , xlim = c(0,1)
#        , ylim = c(0,1)
#        , col = cols
#        , xlab = 'prop 2afc correct'
#        , ylab = 'recall rate'
#        , main = c('sub', as.character(sub))
#   )
#   #legend("topleft", legend = studyConds,
#    #      col=cols,pch = 1,bty="n")
#   
# }

```


```{r,echo=FALSE,warning=FALSE}
# pas.mean_cfs.item = array(999,c(nPresent,nSubs,nItems))
# pas.n_cfs.item = array(999,c(nPresent,nSubs,nItems))
# for (sub in 1:nSubs){
#   for (item in 1:nItems) {
#     
#     if (data_trim[data_trim$whichItem==item
#              & data_trim$subject==sub
#              ,]$condition==3){
#       
#       # first present
#       pas.mean_cfs.item[1,sub,item] <- 
#         data_trim[data_trim$condition==3
#              & data_trim$subject==sub
#              & data_trim$whichItem==item,]$studyResp-1
#       
#       pas.n_cfs.item[1,sub,item] <- 
#         dim(data_trim[data_trim$condition==3
#                  & data_trim$subject==sub
#                  & data_trim$whichItem==item,])[1]
#       
#       
#       # second present
#       pas.mean_cfs.item[2,sub,item] <- 
#         data_trim[data_trim$condition==3
#              & data_trim$subject==sub
#              & data_trim$whichItem==item,]$studyResp2-1
#       
#       pas.n_cfs.item[2,sub,item] <- 
#         dim(data_trim[data_trim$condition==3
#                  & data_trim$subject==sub
#                  & data_trim$whichItem==item,])[1]
#       
#       # third present
#       pas.mean_cfs.item[3,sub,item] <- 
#         data_trim[data_trim$condition==3
#              & data_trim$subject==sub
#              & data_trim$whichItem==item,]$studyResp3-1
#       
#       pas.n_cfs.item[3,sub,item] <- 
#         dim(data_trim[data_trim$condition==3
#                  & data_trim$subject==sub
#                  & data_trim$whichItem==item,])[1]
#     }
#   }
#   
# }
```


```{r,echo=FALSE}
# pas_sub_item_plot = array(999,c(nPresent,48*nSubs))
# item = 0
# for (sub in 1:nSubs){
#   for (trl in 1:nItems){
#     
#     if((pas.mean_cfs.item[,sub,trl])!=999){
#       item = item+1
#       pas_sub_item_plot[,item] <- pas.mean_cfs.item[,sub,trl]
#     }
#   }
# }


```


```{r,echo=FALSE,warning=FALSE}
# par(mfrow=c(1,1))
# df <- data.frame(first = pas_sub_item_plot[1,]
#                  ,second = pas_sub_item_plot[2,]
#                  ,sub=rep(1:6,each=48))
# 
# numPlot<-ggplot(data = df,aes(x = first,y = second)) + stat_sum(aes(size = ..n..))
# numPlot + ggtitle("num(PAS 2 & PAS 1) of items under cfs, all subs")
# 

```

```{r, echo=FALSE,warning=FALSE}
pasCondi.mean.item = array(999,c(nSubs,nPAS,nItems))
pasCondi.n.item = array(999,c(nSubs,nPAS,nItems))
for (sub in 1:nSubs){
  for (pas in 1:nConds){
    for (item in 1:nItems) {
      
      if (length(data_trim[data_trim$whichItem==item
                      & data_trim$subject==sub
                      & data_trim$condition==3
                      ,]$studyResp==pas)!=0 
          && data_trim[data_trim$whichItem==item
                 & data_trim$subject==sub
                 & data_trim$condition==3
                 ,]$studyResp==pas) {
        
        
        # given first resp of pas, what was third?
        pasCondi.mean.item[sub,pas,item] <- 
          data_trim[data_trim$studyResp==pas
               & data_trim$condition==3
               & data_trim$subject==sub
               & data_trim$whichItem==item,]$studyResp3-1
        
        pasCondi.n.item[sub,pas,item] <- 
          dim(data_trim[data_trim$studyResp==pas
                   & data_trim$condition==3
                   & data_trim$subject==sub
                   & data_trim$whichItem==item,])[1]
        
      }
    }
  }
}

pas_condi_plot = array(999,c(48*nSubs,nPAS))
item = 0
for (sub in 1:nSubs){
  for (pas in 1:nPAS){
    for (trl in 1:nItems){
      
      if(!is.na(pasCondi.mean.item[sub,pas,trl])){
        if((pasCondi.mean.item[sub,pas,trl])!=999){
          item = item+1
          pas_condi_plot[item,pas] <- pasCondi.mean.item[sub,pas,trl]
        }
      }
    }
  }
}

# final form?
tally <- array(0,c(nPAS,nPAS))
sum(pas_condi_plot[,1]==3)

for (pas in 1:nPAS){
  for(sec in 1:nPAS){
  tally[pas,sec] <- sum(pas_condi_plot[,pas]==sec-1)
  }
}


barplot(t(tally)
        , beside = TRUE
        , main = "num(PAS_3 | PAS_1)"
        , legend.text = c('to 0', 'to 1', 'to 2', 'to 3')
        , args.legend = list(x="topleft")
        , names.arg = c('0', '1', '2', '3')
)

tally_prop <- tally/rowSums(tally)

```

In the following graph, note that the highest of each group of bars shifts one bar to the right for each gropu (0-3). This says that, for a PAS of 3 on the first presentation, the most likely PAS on the second is 3. Similarly, for a PAS of 2 on the first presentation, the most likely is a 2 on the second (followed by a 1). For 1 on the first, mostly likely is a second 1 (followed by 2). For 0, the most likely is split between 0 and 1.
```{r,echo=FALSE,warning=FALSE}
barplot(t(tally_prop)
        , beside = TRUE
        , main = "p(PAS_3 | PAS_1)"
        , ylim = c(0,1)
        , legend.text = c('to 0', 'to 1', 'to 2', 'to 3')
        , args.legend = list(x="topleft")
        , names.arg = c('0', '1', '2', '3')
)


```
