---
title: "testing"
author: "pss"
date: "February 3, 2016"
output: pdf_document
---




```{r,echo=FALSE,warning=FALSE}
pas.mean_cfs.item = array(999,c(nPresent,nSubs,nItems))
pas.n_cfs.item = array(999,c(nPresent,nSubs,nItems))
for (sub in 1:nSubs){
  for (item in 1:nItems) {
    
    if (data[data$whichItem==item
             & data$subject==sub
             ,]$condition==3){
      
      # first present
      pas.mean_cfs.item[1,sub,item] <- 
        data[data$condition==3
             & data$subject==sub
             & data$whichItem==item,]$studyResp-1
      
      pas.n_cfs.item[1,sub,item] <- 
        dim(data[data$condition==3
                 & data$subject==sub
                 & data$whichItem==item,])[1]
      
      
      # second present
      pas.mean_cfs.item[2,sub,item] <- 
        data[data$condition==3
             & data$subject==sub
             & data$whichItem==item,]$studyResp2-1
      
      pas.n_cfs.item[2,sub,item] <- 
        dim(data[data$condition==3
                 & data$subject==sub
                 & data$whichItem==item,])[1]
      
      
      # third present
      pas.mean_cfs.item[3,sub,item] <- 
        data[data$condition==3
             & data$subject==sub
             & data$whichItem==item,]$studyResp3-1
      
      pas.n_cfs.item[3,sub,item] <- 
        dim(data[data$condition==3
                 & data$subject==sub
                 & data$whichItem==item,])[1]
    }
  }
  
}

pas_sub_item_plot = array(999,c(nPresent,nInCond*nSubs))
item = 0
for (sub in 1:nSubs){
  for (trl in 1:nItems){
    
    if((pas.mean_cfs.item[,sub,trl])!=999){
      item = item+1
      pas_sub_item_plot[,item] <- pas.mean_cfs.item[,sub,trl]
    }
  }
}


```


```{r,echo=FALSE,warning=FALSE}
par(mfrow=c(1,1))
df <- data.frame(first = pas_sub_item_plot[1,]
                 ,second = pas_sub_item_plot[2,]
                 ,sub=rep(1:6,each=50))

numPlot<-ggplot(data = df,aes(x = first,y = second)) + stat_sum(aes(size = ..n..))
numPlot + ggtitle("num(PAS 2 & PAS 1) of items under cfs, all subs")


```

```{r, echo=FALSE,warning=FALSE}
pasCondi.mean.item = array(999,c(nSubs,nPAS,nItems))
pasCondi.n.item = array(999,c(nSubs,nPAS,nItems))
for (sub in 1:nSubs){
  for (pas in 1:nConds){
    for (item in 1:nItems) {
      
      if (length(data[data$whichItem==item
                      & data$subject==sub
                      & data$condition==3
                      ,]$studyResp==pas)!=0 
          && data[data$whichItem==item
                 & data$subject==sub
                 & data$condition==3
                 ,]$studyResp==pas) {
        
        
        # given first resp of pas, what was third?
        pasCondi.mean.item[sub,pas,item] <- 
          data[data$studyResp==pas
               & data$condition==3
               & data$subject==sub
               & data$whichItem==item,]$studyResp3-1
        
        pasCondi.n.item[sub,pas,item] <- 
          dim(data[data$studyResp==pas
                   & data$condition==3
                   & data$subject==sub
                   & data$whichItem==item,])[1]
        
      }
    }
  }
}

pas_condi_plot = array(999,c(nInCond*nSubs,nPAS))
item = 0
for (sub in 1:nSubs){
  for (pas in 1:nPAS){
    for (trl in 1:nItems){
      
      if(!is.na(pasCondi.mean.item[sub,pas,trl])){
        if((pasCondi.mean.item[sub,pas,trl])!=999){
          item = item+1
          pas_condi_plot[item,pas] <- pasCondi.mean.item[sub,pas,trl]
        }
      }
    }
  }
}

# final form?
tally <- array(0,c(nPAS,nPAS))
sum(pas_condi_plot[,1]==3)

for (pas in 1:nPAS){
  for(sec in 1:nPAS){
  tally[pas,sec] <- sum(pas_condi_plot[,pas]==sec-1)
  }
}


barplot(t(tally)
        , beside = TRUE
        , main = "num(PAS_2 | PAS_1)"
        , legend.text = c('to 0', 'to 1', 'to 2', 'to 3')
        , args.legend = list(x="topleft")
        , names.arg = c('0', '1', '2', '3')
)

tally_prop <- tally/rowSums(tally)

```

In the following graph, note that the highest of each group of bars shifts one bar to the right for each gropu (0-3). This says that, for a PAS of 3 on the first presentation, the most likely PAS on the second is 3. Similarly, for a PAS of 2 on the first presentation, the most likely is a 2 on the second (followed by a 1). For 1 on the first, mostly likely is a second 1 (followed by 2). For 0, the most likely is split between 0 and 1.
```{r,echo=FALSE,warning=FALSE}
barplot(t(tally_prop)
        , beside = TRUE
        , main = "p(PAS_2 | PAS_1)"
        , ylim = c(0,1)
        , legend.text = c('to 0', 'to 1', 'to 2', 'to 3')
        , args.legend = list(x="topleft")
        , names.arg = c('0', '1', '2', '3')
)


```
