---
title: "CFS, 2AFC, Short Study Lists, w/FeedBack"
author: "pss"
date: "March 2, 2016"
output: pdf_document
---

summary of results for cfs study

Version: presentation in lists of 16. Items studied x3 times 
Note that second/third presentation was in the same order as first presentations
all items studied for total of .5 seconds (including ramping up and down)

these data include subjects that didn't provide many recall choices

```{r, preamble, echo=FALSE,warning=FALSE}
# preamble

library(ggplot2)
library(plyr)
library(gridExtra)
source("C:/Users/admin/Documents/R/fns.R")

setwd("C:/Users/admin/googleDrive/uMass/firstYear/behavioralExpts/pSadil/processDissociation/CFS/cfs_fg/analysisCode/R/afc/shortStudyLists_wFB")



# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

```{r,data,echo=FALSE,warning=FALSE}
# preliminary changing of folders
#setwd("D:/googleDrive/uMass/firstYear/behavioralExpts/pSadil/processDissociation/CFS/analysisCode/R/afc/shortStudyLists")

wd <- getwd()

dataFile <- paste(wd, "/cfs_obj_2afc_ss1_wFB_noCheck.dat", sep="")
# find the data that was generated from the matlab files
data <- read.csv(dataFile)

# add 1 to study resp because participants were instructed to use 0-3

#data[data$studyResp3==1e+05,]$studyResp3 = 1
#data$studyResp3 <- as.factor(data$studyResp3)


nConds = max(data$condition,na.rm=TRUE)
nPAS = max(data[data$studyResp < 1000,]$studyResp,na.rm=TRUE) + 1
nItems = max(data$whichItem,na.rm=TRUE)
nSubs = max(data$subject,na.rm=TRUE)
nTrials = max(data$trial,na.rm=TRUE)
nInCond = nItems / nConds

# number of items in each condition, first presentation
nPerCond = nItems/nConds

data[data$condition==1,]$condition = 'a_foil'
data[data$condition==2,]$condition = 'b_word'
data[data$condition==3,]$condition = 'c_cfs'
data[data$condition==4,]$condition = 'd_binocular'



data$trial = as.factor(data$trial)
data$whichItem = as.factor(data$whichItem)
data$subject = as.factor(data$subject)
data$condition = as.factor(data$condition)
data$studyResp = as.factor(data$studyResp)
data$studyResp2 = as.factor(data$studyResp2)
data$studyResp3 = as.factor(data$studyResp3)


#data$condition = as.numeric(data$condition)
# don't want PAS as a factor, because there are 
# vastly different numbers of each kind of response
# Do I want condition as factor? if it were, that would
# seem to make stronger claims (justified) about higher levels
# leading to higher recall rates
studyConds <- c("foil","word","cfs","binoc")
cols <- c('black', 'cornflowerblue', 'darkgoldenrod1', 'red')
pasResps <- c("0","1","2","3")

# trim away missing values (there aren't, currently)
data_trim <- na.omit(data)


cutoff = 3 # only look at CFS with PAS 2 or 1
nPresent = 3 # presented 3 times
nStudy = nTrials * nPresent

pd <- position_dodge(0.001)
```


```{r, withinErrorBars, echo=FALSE,warning=FALSE}

# name_pas4 <- withinSubError(data_trim,4,nConds)
# name_pas3 <- withinSubError(data_trim,3,nConds)
# name_pas2 <- withinSubError(data_trim,2,nConds)
# name_pas1 <- withinSubError(data_trim,1,nConds)
# sem <- rbind(name_pas1$sem_cf,name_pas2$sem_cf,name_pas3$sem_cf,name_pas4$sem_cf)
# tPlot <- rbind(name_pas1$y_sj,name_pas2$y_sj,name_pas3$y_sj,name_pas4$y_sj)
# 
# data_plot <- data_trim
# data_plot[data_plot$studyResp3==1e+05,]$studyResp3 = 1
# data_plot$studyResp3 <- as.factor(data_plot$studyResp3)
# #data_plot$studyResp3 == as.double(data_plot$studyResp3)
# 


dfwc3 <- summarySEwithin(data, measurevar="named"
                         , withinvars=c("condition","studyResp3"),
                         idvar="subject", na.rm=FALSE, conf.interval=.95)
dfwc3<-ddply(dfwc3,.(condition),transform,prop=N/sum(N))

dfwc1 <- summarySEwithin(data, measurevar="named"
                         , withinvars=c("condition","studyResp"),
                         idvar="subject", na.rm=FALSE, conf.interval=.95)
dfwc1<-ddply(dfwc1,.(condition),transform,prop=N/sum(N))

```


## CFS masking results

NOTE: 

1. in these bar graphs, 1e+05 indicates the value that was given to foils (so, there should only be bars over the 1e+05 studyResp for the foil condition).
2. the NA studyResp are missing responses.
3. although these error bars more accurately reflect the within-subjects nature of the study condition factor, the y-axis is still bounded between [0,1]. So, I still need to figure out a reasonable way to plot those values...


```{r,echo=FALSE,warning=FALSE}
ggplot(dfwc3, aes(x=studyResp3, y=named)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  geom_errorbar(width=.25, aes(ymin=named-ci, ymax=named+ci)) +
  facet_grid(. ~ condition ) +
  xlab("PAS") + 
  ylab("named") +
  ggtitle("% named for each condition, given third PAS")

```

```{r,echo=FALSE,warning=FALSE}
ggplot(dfwc3, aes(x=studyResp3, y=prop)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  geom_errorbar(width=.25, aes(ymin=prop-ci, ymax=prop+ci)) +
  facet_grid(. ~ condition ) +
  xlab("PAS") + 
  ylab("proportion") +
  ggtitle("proportion of each PAS (third presentation) in each condition")

```


looking at first presentations

```{r,echo=FALSE,warning=FALSE}
ggplot(dfwc1, aes(x=studyResp, y=named)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  geom_errorbar(width=.25, aes(ymin=named-ci, ymax=named+ci)) +
  facet_grid(. ~ condition ) +
  xlab("PAS") + 
  ylab("named") +
  ggtitle("% named for each condition, given first PAS")

```

```{r,echo=FALSE,warning=FALSE}
ggplot(dfwc1, aes(x=studyResp, y=prop)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  geom_errorbar(width=.25, aes(ymin=prop-ci, ymax=prop+ci)) +
  facet_grid(. ~ condition ) +
  xlab("PAS") + 
  ylab("proportion") +
  ggtitle("proportion of each PAS (first presentation) in each condition")

```


```{r, pas_conditional,echo=FALSE,warning=FALSE}
dfwc_pas <- summarySEwithin(data, measurevar="named", withinvars=c("studyResp","studyResp3"),
                            idvar="subject", na.rm=FALSE, conf.interval=.95)

dfwc_pas<-ddply(dfwc_pas,.(studyResp3),transform,p3Gp1=N/sum(N))

dfwc_pas_cfs <- summarySEwithin(data[data$condition=='c_cfs',], measurevar="named",                          withinvars=c("studyResp","studyResp3"),
                                idvar="subject", na.rm=FALSE, conf.interval=.95)

dfwc_pas_cfs<-ddply(dfwc_pas_cfs,.(studyResp3),transform,p3Gp1=N/sum(N))




```


```{r,pas_condi_graph,echo=FALSE,warning=FALSE}

ggplot(dfwc_pas, aes(x=studyResp3, y=p3Gp1)) +
  geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
  facet_grid(. ~ studyResp ) +
  facet_wrap(~ studyResp, ncol=3) +
  xlab("PAS") + 
  ylab("p(PAS_3|PAS_1)") +
  ggtitle(" Proportion of thrid PAS given first PAS ")


```




```{r,pas_condi_,echo=FALSE,warning=FALSE}

# ggplot(dfwc_pas_cfs, aes(x=studyResp3, y=p3Gp1)) +
#   geom_bar(position=position_dodge(.9), colour="black", stat="identity") +
#   facet_grid(. ~ studyResp ) +
#   facet_wrap(~ studyResp, ncol=3) +
#   xlab("PAS") + 
#   ylab("p(PAS_3|PAS_1)") +
#   ggtitle(" Proportion of thrid PAS given first PAS ")


```


## State Trace, overall

now, scatter plots


```{r,stateTrace_avg,warning=FALSE,echo=FALSE}
afc_all <- summarySEwithin(data, measurevar="afc",
                           withinvars=c("condition"),
                           idvar="subject", na.rm=TRUE, conf.interval=.95)

name_all <- summarySEwithin(data, measurevar="named",
                            withinvars=c("condition"),
                            idvar="subject", na.rm=TRUE, conf.interval=.95)


toPlot_stAll <- cbind(named=name_all$named
                      ,named_norm=name_all$named_norm
                      ,ci_named=name_all$ci
                      ,afc_all
                      ,count=(afc_all$N+name_all$N)/2)



# using only data for when PAS == 2
data_trim <- data[(data$studyResp3=="2" & data$condition=='c_cfs') | 
                                    (data$studyResp3=="3" & data$condition=='d_binocular') |
                                    (data$studyResp3=="3" & data$condition=='b_word') |
                                   (data$studyResp3=="99999" & data$condition=='a_foil'),]

afc_trim <- summarySEwithin(data_trim
                            , measurevar="afc",
                           withinvars=c("condition"),
                           idvar="subject", na.rm=TRUE, conf.interval=.95)

name_trim <- summarySEwithin(data_trim
                            , measurevar="named",
                           withinvars=c("condition"),
                           idvar="subject", na.rm=TRUE, conf.interval=.95)

toPlot_stTrim <- cbind(named=name_trim$named
                      ,named_norm=name_trim$named_norm
                      ,ci_named=name_trim$ci
                      ,afc_trim
                      ,count=(afc_trim$N+name_trim$N)/2)

# hack to plot this value
na.rm = FALSE
afc_avgSubFirst <- ddply(data_trim, c('subject','condition'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(subjectMean = mean(xx[,col], na.rm=na.rm))
                         },
                         'afc',
                         na.rm
  )

toPlot_stTrim.afc_avgSub <- ddply(afc_avgSubFirst, c('condition'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(afc_avgSub = mean(xx[,col], na.rm=na.rm))
                         },
                         'subjectMean',
                         na.rm
  )

toPlot_stTrim <- merge(toPlot_stTrim, toPlot_stTrim.afc_avgSub)

named_avgSubFirst <- ddply(data_trim, c('subject','condition'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(subjectMean = mean(xx[,col], na.rm=na.rm))
                         },
                         'named',
                         na.rm
  )

toPlot_stTrim.named_avgSub <- ddply(named_avgSubFirst, c('condition'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(named_avgSub = mean(xx[,col], na.rm=na.rm))
                         },
                         'subjectMean',
                         na.rm
  )

toPlot_stTrim <- merge(toPlot_stTrim, toPlot_stTrim.named_avgSub)


# using only data for when PAS == 0-2
data02 <- data[(data$studyResp3=="2" & data$condition=='c_cfs') |
                                   (data$studyResp3=="0" & data$condition=='c_cfs') |
                                   (data$studyResp3=="1" & data$condition=='c_cfs') |
                                    (data$studyResp3=="3" & data$condition=='d_binocular') |
                                    (data$studyResp3=="3" & data$condition=='b_word') |
                                   (data$studyResp3=="99999" & data$condition=='a_foil'),]

afc_trim02 <- summarySEwithin(data02
                            , measurevar="afc",
                           withinvars=c("condition"),
                           idvar="subject", na.rm=TRUE, conf.interval=.95)

name_trim02 <- summarySEwithin(data02
                             , measurevar="named",
                            withinvars=c("condition"),
                            idvar="subject", na.rm=TRUE, conf.interval=.95)

toPlot_stTrim02 <- cbind(named=name_trim02$named
                      ,named_norm=name_trim02$named_norm
                      ,ci_named=name_trim02$ci
                      ,afc_trim02
                      ,count=(afc_trim02$N+name_trim02$N)/2)



afc02_avgSubFirst <- ddply(data02, c('subject','condition'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(subjectMean = mean(xx[,col], na.rm=na.rm))
                         },
                         'afc',
                         na.rm
  )

toPlot_stTrim02.afc_avgSub <- ddply(afc02_avgSubFirst, c('condition'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(afc02_avgSub = mean(xx[,col], na.rm=na.rm))
                         },
                         'subjectMean',
                         na.rm
  )

toPlot_stTrim02 <- merge(toPlot_stTrim02, toPlot_stTrim02.afc_avgSub)

named02_avgSubFirst <- ddply(data02, c('subject','condition'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(subjectMean = mean(xx[,col], na.rm=na.rm))
                         },
                         'named',
                         na.rm
  )

toPlot_stTrim02.named_avgSub <- ddply(named02_avgSubFirst, c('condition'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(named02_avgSub = mean(xx[,col], na.rm=na.rm))
                         },
                         'subjectMean',
                         na.rm
  )

toPlot_stTrim02 <- merge(toPlot_stTrim02, toPlot_stTrim02.named_avgSub)




```


```{r,st_plot_avg,warning=FALSE,echo=FALSE,fig.height=10, out.height='10in', fig.align='center'}
pd <- position_dodge(0.001)

ggplot(toPlot_stAll, aes(x=afc, y=named, colour=condition, group=condition)) +
  geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
  # ylim(0,1) +
  # xlim(0,1) +
  geom_point(position=pd, size=1)  +  #aes(size=count)
      coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  scale_y_continuous(breaks=seq(from=0, to=1, by=0.25)) +
  ggtitle("state trace, for each condition, collapsed across PAS/presentations") +
  theme(aspect.ratio = 1) +
  # theme(axis.ticks = element_blank(), axis.text.x = element_blank()) +
  theme(axis.ticks = element_blank())



```

what follows is a state trace in which items that went in to the cfs condition were given a 2 on the third pas, but items in the word and binocular conditions were given a 3

```{r trimmed,warning=FALSE}
 # note that many fewer data points go in to the CFS point (pay attention to the 'count' column)
toPlot_stTrim

```

```{r,st_plot_trim,warning=FALSE,echo=FALSE,fig.height=10, out.height='10in', fig.align='center'}

ggplot(toPlot_stTrim, aes(x=afc_avgSub, y=named_avgSub, colour=condition, group=condition)) +
  geom_errorbar(aes(ymin=named_avgSub-ci_named, ymax=named_avgSub+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc_avgSub-ci, xmax=afc_avgSub+ci), colour="black", height = .05, position=pd) +
  # ylim(0,1) +
  # xlim(0,1) +
  geom_point(position=pd, size=1)  +  #aes(size=count)
      coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  scale_y_continuous(breaks=seq(from=0, to=1, by=0.25)) +
  ggtitle("state trace, conditions depend on PAS") +
  theme(aspect.ratio = 1) +
  # theme(axis.ticks = element_blank(), axis.text.x = element_blank()) +
  theme(axis.ticks = element_blank())



```

# the same graph, but the cfs condition contains pas ratings of 0-2
there is much more data in the cfs points here

```{r warning=FALSE}
toPlot_stTrim02
```


```{r,st_plot_trim02,warning=FALSE,echo=FALSE,fig.height=10, out.height='10in', fig.align='center'}

ggplot(toPlot_stTrim02, aes(x=afc02_avgSub, y=named02_avgSub, colour=condition, group=condition)) +
  geom_errorbar(aes(ymin=named02_avgSub-ci_named, ymax=named02_avgSub+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc02_avgSub-ci, xmax=afc02_avgSub+ci), colour="black", height = .05, position=pd) +
  # ylim(0,1) +
  # xlim(0,1) +
  geom_point(position=pd, size=1)  +  #aes(size=count)
      coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  scale_y_continuous(breaks=seq(from=0, to=1, by=0.25)) +
  ggtitle("state trace, conditions depend on PAS") +
  theme(aspect.ratio = 1) +
  # theme(axis.ticks = element_blank(), axis.text.x = element_blank()) +
  theme(axis.ticks = element_blank())



```






```{r,echo=FALSE,warning=FALSE}
# state trace plots


dfwc3_afc <- summarySEwithin(data, measurevar="afc"                       , withinvars=c("condition","studyResp3"),
                             idvar="subject", na.rm=TRUE, conf.interval=.95)

toPlot3 <- cbind(named=dfwc3$named,ci_named=dfwc3$ci
                 ,dfwc3_afc,count=(dfwc3$N+dfwc3_afc$N)/2)


dfwc1_afc <- summarySEwithin(data, measurevar="afc"                       , withinvars=c("condition","studyResp"),
                             idvar="subject", na.rm=TRUE, conf.interval=.95)

toPlot1 <- cbind(named=dfwc1$named,ci_named=dfwc1$ci
                 ,dfwc1_afc,count=(dfwc1$N+dfwc1_afc$N)/2)


```



```{r,scatterPlots_third_noSize,echo=FALSE,warning=FALSE,fig.height=10, out.height='10in', fig.align='center'}

ggplot(toPlot3, aes(x=afc, y=named, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
  # ylim(0,1) +
  # xlim(0,1) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  geom_point(position=pd, size=1) +
  facet_grid(. ~ studyResp3 ) +
  facet_wrap(~ studyResp3, ncol=3) +
  ggtitle("state trace, facets indicate PAS response on third presentation (99999 => foil)") +
  theme(aspect.ratio = 1) 



```



```{r,scatterPlots_third,echo=FALSE,warning=FALSE,fig.height=10, out.height='10in', fig.align='center'}


ggplot(toPlot3, aes(x=afc, y=named, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
  # ylim(0,1) +
  # xlim(0,1) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  geom_point(position=pd, aes(size=count)) +
  scale_size_continuous(breaks=c(10,100,200,400,600)) +
  facet_grid(. ~ studyResp3 ) +
  facet_wrap(~ studyResp3, ncol=3) +
  ggtitle("state trace, facets indicate PAS response on third presentation (99999 => foil)") +
  theme(aspect.ratio = 1) 



```


In the above graph, size of dot indicates amount of data going in to point

```{r,scatterPlots_first,echo=FALSE,warning=FALSE,fig.height=10, out.height='10in', fig.align='center'}

ggplot(toPlot1, aes(x=afc, y=named, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
  # ylim(0,1) +
  # xlim(0,1) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  geom_point(position=pd, aes(size=count))  +
  scale_size_continuous(breaks=c(10,100,200,400,600)) +
  facet_grid(. ~ studyResp ) +
  facet_wrap(~ studyResp, ncol=3) +
  ggtitle("state trace, facets indicate PAS response on first presentation (99999 => foil)") +
  theme(aspect.ratio = 1)


```

## Subjects

now, look at individual subjects (normalized scores)
NOTE: the normalized and raw scores look similar, but they are at least a little bit different in each graph
 - the raw numbers are printed at the bottom of the document

```{r,subData,echo=FALSE,warning=FALSE}
afc_sub <- summarySEwithin(data, measurevar="afc",
                           withinvars=c("condition","subject"),
                           idvar="subject", na.rm=TRUE, conf.interval=.95)

name_sub <- summarySEwithin(data, measurevar="named",
                            withinvars=c("condition","subject"),
                            idvar="subject", na.rm=TRUE, conf.interval=.95)


toPlot_sub <- cbind(named=name_sub$named
                    ,named_norm=name_sub$named_norm
                    ,ci_named=name_sub$ci
                    ,afc_sub
                    ,count=(afc_sub$N+name_sub$N)/2)



```


```{r,st_sub_graph1,echo=FALSE,warning=FALSE,fig.height=10, out.height='10in', fig.align='center'}
ggplot(toPlot_sub, aes(x=afc_norm, y=named_norm, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named_norm-ci_named, ymax=named_norm+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc_norm-ci, xmax=afc_norm+ci), colour="black", height = .05, position=pd) +
  # ylim(0,1) +
  # xlim(0,1) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  scale_y_continuous(breaks=c(0,1)) +
  scale_x_continuous(breaks=c(0,1)) +
  geom_point(position=pd, size=1)  +  #aes(size=count)
  #  scale_size_continuous(breaks=c(10,100,200,400,600)) +
  facet_grid(. ~ subject ) +
  facet_wrap(~ subject, ncol=5) +
  ggtitle("state trace, by subject, normalized scores") +
  theme(aspect.ratio = 1) +
  theme(axis.ticks = element_blank())
  # theme(axis.ticks = element_blank(), axis.text.y = element_blank())


```


```{r,st_sub_graph2,echo=FALSE,warning=FALSE, fig.height=10, out.height='10in', fig.align='center'}
pd <- position_dodge(0.001)

ggplot(toPlot_sub, aes(x=afc, y=named, colour=condition, group=condition)) + 
  geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
  geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
  # ylim(0,1) +
  # xlim(0,1) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  scale_y_continuous(breaks=c(0,1)) +
  scale_x_continuous(breaks=c(0,1)) +
  geom_point(position=pd, size=1)  +  #aes(size=count)
  #  scale_size_continuous(breaks=c(10,100,200,400,600)) +
  facet_grid(. ~ subject ) +
  facet_wrap(~ subject, ncol=5) +
  ggtitle("state trace, by subject, raw scores") +
  theme(aspect.ratio = 1) +
  theme(axis.ticks = element_blank())
  # theme(axis.ticks = element_blank(), axis.text.y = element_blank())


```


## Items


```{r items,warning=FALSE,echo=FALSE,fig.height=10, out.height='10in', fig.align='center'}
first <- seq(from=1, to = nItems, by = 16)
second <- seq(from=16, to = nItems, by = 16)
nBlocks <- nItems / 16


  items_named <- summarySEwithin(data, measurevar="named"
                                 , withinvars=c("condition","whichItem"),
                                 idvar="whichItem", na.rm=FALSE, conf.interval=.95)

  items_afc <- summarySEwithin(data, measurevar="afc"
                               , withinvars=c("condition","whichItem"),
                               idvar="whichItem", na.rm=FALSE, conf.interval=.95)

  toPlot_item <- cbind(named=items_named$named
                       ,named_norm=items_named$named_norm
                       ,ci_named=items_named$ci
                       ,items_afc
                       ,count=(items_afc$N+items_named$N)/2)

  
    items_named_avg <- summarySEwithin(data, measurevar="named"
                                 , withinvars=c("whichItem"),
                                 idvar="whichItem", na.rm=FALSE, conf.interval=.95)

  items_afc_avg <- summarySEwithin(data, measurevar="afc"
                               , withinvars=c("whichItem"),
                               idvar="whichItem", na.rm=FALSE, conf.interval=.95)

  toPlot_item_avg <- cbind(named=items_named_avg$named
                       ,named_norm=items_named_avg$named_norm
                       ,ci_named=items_named_avg$ci
                       ,items_afc_avg
                       ,count=(items_afc_avg$N+items_named_avg$N)/2)
  

```

plotting performance for all items
NOTE: item positions do not line up across grids. That is, a point that appears to be in the same place on all for grids may be from different items. These graphs tell us, when an item was ina given condition, how often it was named and how often people picked the correct pair in the afc

```{r warning=FALSE,echo=FALSE,fig.height=10, out.height='8in', fig.align='center'}

  ggplot(toPlot_item, aes(x=afc, y=named, colour=condition, group=condition)) +
    geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
    geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
    geom_point(position=pd, size=2)  +  # count
     # scale_size_continuous(breaks=c(50,100,150,200)) +
    facet_grid(. ~ condition ) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  scale_y_continuous(breaks=c(0,1)) +
  scale_x_continuous(breaks=c(0,1)) +
    facet_wrap(~ condition, ncol=2) +
    ggtitle("state trace, for each items") +
      # ylim(0,1) +
    # xlim(0,1) +
    theme(aspect.ratio = 1) +
    theme(axis.ticks = element_blank())
    # theme(axis.ticks = element_blank(), axis.text.y = element_blank())


```


same plot as above, but without the error bars for easier viewing

```{r warning=FALSE,echo=FALSE,fig.height=10, out.height='8in', fig.align='center'}

  ggplot(toPlot_item, aes(x=afc, y=named, colour=condition, group=condition)) +
    # geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
    # geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
    geom_point(position=pd, size=2)  +  # count
     # scale_size_continuous(breaks=c(50,100,150,200)) +
    facet_grid(. ~ condition ) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  scale_y_continuous(breaks=c(0,1)) +
  scale_x_continuous(breaks=c(0,1)) +
    facet_wrap(~ condition, ncol=2) +
    ggtitle("state trace, for each items") +
      # ylim(0,1) +
    # xlim(0,1) +
    theme(aspect.ratio = 1) +
    theme(axis.ticks = element_blank())
    # theme(axis.ticks = element_blank(), axis.text.y = element_blank())


```


item rates, collapsed across all conditions
count = 29 because there are 29 subjects

```{r warning=FALSE,echo=FALSE,fig.height=10, out.height='7in', fig.align='center'}

  ggplot(toPlot_item_avg, aes(x=afc, y=named)) +
    geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
    geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
    geom_point(position=pd, aes(size=count))  +  # count
     # scale_size_continuous(breaks=c(50,100,150,200)) +
    # facet_grid(. ~ condition ) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  scale_y_continuous(breaks=c(0,1)) +
  scale_x_continuous(breaks=c(0,1)) +
    # facet_wrap(~ condition, ncol=2) +
    ggtitle("state trace, for each item") +
      # ylim(0,1) +
    # xlim(0,1) +
    theme(aspect.ratio = 1) +
    theme(axis.ticks = element_blank())
    # theme(axis.ticks = element_blank(), axis.text.y = element_blank())


```


same as above, without error bars


```{r warning=FALSE,echo=FALSE,fig.height=10, out.height='7in', fig.align='center'}

  ggplot(toPlot_item_avg, aes(x=afc, y=named)) +
    # geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
    # geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
    geom_point(position=pd, aes(size=count))  +  # count
     # scale_size_continuous(breaks=c(50,100,150,200)) +
    # facet_grid(. ~ condition ) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0,1)) +
  scale_y_continuous(breaks=c(0,1)) +
  scale_x_continuous(breaks=c(0,1)) +
    # facet_wrap(~ condition, ncol=2) +
    ggtitle("state trace, for each item") +
      # ylim(0,1) +
    # xlim(0,1) +
    theme(aspect.ratio = 1) +
    theme(axis.ticks = element_blank())
    # theme(axis.ticks = element_blank(), axis.text.y = element_blank())


```




```{r itemsLogit, warning=FALSE,echo=FALSE,fig.height=10, out.height='7in', fig.align='center'}
na.rm = TRUE
toPlot_item_avg.namedLogit <- ddply(toPlot_item_avg, c('whichItem'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(namedLogit = logit(xx[,col]))
                         },
                         'named',
                         na.rm
  )
toPlot_item_avg.afcLogit <- ddply(toPlot_item_avg, c('whichItem'), .drop=TRUE,
                         .fun = function(xx, col, na.rm) {
                           c(afcLogit = logit(xx[,col]))
                         },
                         'afc',
                         na.rm
)

toPlot_item_avg <- merge(toPlot_item_avg, toPlot_item_avg.namedLogit)
toPlot_item_avg <- merge(toPlot_item_avg, toPlot_item_avg.afcLogit)


  ggplot(toPlot_item_avg[toPlot_item_avg$afcLogit != Inf & toPlot_item_avg$namedLogit != -Inf & toPlot_item_avg$namedLogit != Inf,], aes(x=afcLogit, y=namedLogit)) +
    # geom_errorbar(aes(ymin=named-ci_named, ymax=named+ci_named), colour="black", width=.05, position=pd) +
    # geom_errorbarh(aes(xmin=afc-ci, xmax=afc+ci), colour="black", height = .05, position=pd) +
    geom_point(position=pd, aes(size=count))  +  # count
  coord_cartesian(xlim = c(-4, 4), ylim = c(-4,4)) +
  scale_y_continuous(breaks=c(-4,4)) +
  scale_x_continuous(breaks=c(-4,4)) +
    ggtitle("state trace, item, logit transformed scores") +
    theme(aspect.ratio = 1) +
    theme(axis.ticks = element_blank())


```


## items again

These are a rank order of the items that benefitted most from study in the CFS condition

```{r,echo=FALSE, warning=FALSE}
library(dplyr)
```

 -  line indicates no benefit of binocular study. Above line indicates positive benefit, below line indicates worse performance after study

```{r, itemBene}

tmp <- filter(toPlot_item, condition %in% c('a_foil', 'd_binocular' ))

tmpBinoc <- filter(tmp, condition == 'd_binocular') %>%
  select(., afc, named,whichItem)
  
tmpFoil <- filter(tmp, condition == 'a_foil') %>%
  select(., afc, named,whichItem)

full <- cbind(tmpBinoc[,1:2] - tmpFoil[,1:2], item = tmpBinoc[,3]) %>%
  arrange(., desc(afc),desc(named))


plot(tmpFoil$afc, tmpBinoc$afc
     , xlab = 'foil'
     , ylab = 'binocular'
     , main = 'afc in different conditions'
     , ylim = c(0,1)
     , xlim = c(0,1)
     )
abline(0,1)

full

```



```{r,named}
# collapsed across subjects, grouped by condition and pas response to the first study
dfwc1 

# collapsed across subjects, grouped by condition and pas response to the third study
dfwc3

# data for every subject, grouped by condition, collapsed across all pas ratings for all three study presentations
toPlot_sub
```
