---
title: "CFS, 2AFC, Double Study"
author: "pss"
date: "December 14, 2015"
output: pdf_document
---

summary of results for cfs study

Version: double presentation of all 200 study items 
  Note that second presentation was in the same order as first presentation
  all items studied for total of .5 seconds (including ramping up and down)



```{r,echo=FALSE}
# preamble


library(ggplot2)


error.bar <- function(x, y, upper, lower=upper, length=0.1,...){
  if(length(x) != length(y) | length(y) !=length(lower) | length(lower) != length(upper))
    stop("vectors must be same length")
  arrows(x,y+upper, x, y-lower, angle=90, code=3, length=length, ...)
}

setwd("D:/googleDrive/uMass/firstYear/behavioralExpts/pSadil/processDissociation/CFS/analysisCode/R/afc/doubleStudy")
wd <- getwd()

dataFile <- paste(wd, "/cfs_obj_2afc.dat", sep="")
# find the data that was generated from the matlab files
data <- read.csv(dataFile)

# add 1 to study resp because participants were instructed to use 0-3
data$studyResp = data$studyResp+1
data$studyResp2 = data$studyResp2+1

nConds = max(data$condition,na.rm=TRUE)
nPAS = max(data[data$studyResp < 1000,]$studyResp,na.rm=TRUE)
nItems = max(data$whichItem,na.rm=TRUE)
nSubs = max(data$subject,na.rm=TRUE)
nTrials = max(data$trial,na.rm=TRUE)

# number of items in each condition, first presentation
nPerCond = nItems/nConds


data$trial = as.factor(data$trial)
data$whichItem = as.factor(data$whichItem)
data$subject = as.factor(data$subject)
data$condition = as.factor(data$condition)


studyConds <- c("foil","word","cfs","binoc")
cols <- c('black', 'cornflowerblue', 'darkgoldenrod1', 'red')
pasResps <- c("0","1","2","3")

# trim away missing values
data_trim <- na.omit(data)


```


```{r}
cutoff <- 3
nPresent = 2
nStudy = nTrials * nPresent
```

```{r, echo=FALSE}
rRates.pasCond_mean = array(0,dim=c(nConds,nPAS,2))
rRates.pasCond_sem = array(0,dim=c(nConds,nPAS,2))
rRates.pasCond_n = array(0,dim=c(nConds,nPAS,2))
for (cond in 1:nConds) {
  for (pas in 1:nPAS) {
    
    rRates.pasCond_mean[cond,pas,1] <- 
      mean(data_trim[data_trim$condition==cond &
                       data_trim$studyResp==pas,]$named,
           na.rm=TRUE)
    
    rRates.pasCond_n[cond,pas,1] <- 
      dim(data_trim[data_trim$condition==cond & 
                      data_trim$studyResp==pas,])[1]
    
    # var = n*p*(1-p)
    rRates.pasCond_sem[cond,pas,1] <-
      sqrt(rRates.pasCond_n[cond,pas,1] * rRates.pasCond_mean[cond,pas,1] * 
             (1- rRates.pasCond_mean[cond,pas,1])) / 
      sqrt(rRates.pasCond_n[cond,pas,1])
    
    
    # second presentation
    rRates.pasCond_mean[cond,pas,2] <- 
      mean(data_trim[data_trim$condition==cond &
                       data_trim$studyResp2==pas,]$named,
           na.rm=TRUE)
    
    rRates.pasCond_n[cond,pas,2] <- 
      dim(data_trim[data_trim$condition==cond & 
                      data_trim$studyResp2==pas,])[1]
    
    rRates.pasCond_sem[cond,pas,2] <-
      sqrt(rRates.pasCond_n[cond,pas,2] * rRates.pasCond_mean[cond,pas,2] * 
             (1- rRates.pasCond_mean[cond,pas,2])) / 
      sqrt(rRates.pasCond_n[cond,pas,2])
    
  }
}

rRates.pasCond_n.prop = array(0,dim=c(nConds,nPAS,2))
for (cond in 1:nConds) {
  for (pas in 1:nPAS){
    rRates.pasCond_n.prop[cond,pas,1] <- 
      rRates.pasCond_n[cond,pas,1] / 
      sum(rRates.pasCond_n[cond,,1])
    
    # second presentation
    rRates.pasCond_n.prop[cond,pas,2] <- 
      rRates.pasCond_n[cond,pas,2] / 
      sum(rRates.pasCond_n[cond,,2])
  }
}

```
 
 
The following is a graph of the proportion of times that an item was named,
conditioned on a given PAS response.

Note that eror bars are weird because they're just simple SEMs. Currently unclear about 
the best ways to make error bars for variables bounded between 1 and 0.

```{r,echo=FALSE,warning=FALSE}
par(mfrow=c(1,1))
pasCond.bp <- barplot(t(rRates.pasCond_mean[,,1]),
                  beside=TRUE,
                  names.arg=studyConds,
                  ylim=c(0,1),
                  #col=presentCol,
                  legend.text=pasResps,
                  args.legend = list(x="topleft"),
                  xlab = "study length",
                  ylab = "proportion named"
                  , main = "first presentation"
                  
)
error.bar(pasCond.bp,t(rRates.pasCond_mean[,,1]),
          t(rRates.pasCond_sem[,,1]))



par(mfrow=c(1,1))
pasResps <- c("0","1","2","3")
pasCond.bp <- barplot(t(rRates.pasCond_mean[,,2]),
                  beside=TRUE,
                  names.arg=studyConds,
                  ylim=c(0,1),
                  #col=presentCol,
                  legend.text=pasResps,
                  args.legend = list(x="topleft"),
                  xlab = "study length",
                  ylab = "proportion named"
                  , main = "second presentation"
                  
)
error.bar(pasCond.bp,t(rRates.pasCond_mean[,,2]),
          t(rRates.pasCond_sem[,,2]))

```


Next up is a plot of the proportion of times that an item was given a particular 
PAS rating

```{r,echo=FALSE}

par(mfrow=c(1,1))
# looking at raw numbers of each PAS per condition
pasCond_n.bp <- barplot(t(rRates.pasCond_n.prop[,,1]),
                        beside=TRUE,
                        names.arg=studyConds,
                        ylim=c(0,1),
                        #col=presentCol,
                        legend.text=pasResps,
                        args.legend = list(x="topleft"),
                        xlab = "study length",
                        ylab = "proportion of resposnes"
                        , main = "first presentation"
)


par(mfrow=c(1,1))
# looking at raw numbers of each PAS per condition
pasCond_n.bp <- barplot(t(rRates.pasCond_n.prop[,,2]),
                        beside=TRUE,
                        names.arg=studyConds,
                        ylim=c(0,1),
                        #col=presentCol,
                        legend.text=pasResps,
                        args.legend = list(x="topleft"),
                        xlab = "study length",
                        ylab = "proportion of resposnes"
                        , main = "second presentation"
)


```

next, look at the scatter plots

```{r,echo=FALSE}
# look at recal rates for pas < cutoff, collapsed across subs
rRates.cond_mean = matrix(0,nrow=nConds,ncol=2)
rRates.cond_sem = matrix(0,nrow=nConds,ncol=2)
rRates.cond_n = matrix(0,nrow=nConds,ncol=2)
for (cond in 1:nConds) {
  
  if (cond == 3){
    rRates.cond_mean[cond,1] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp < cutoff),]$named,
           na.rm=TRUE)
    
    rRates.cond_n[cond,1] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp < cutoff ),])[1]
    
    rRates.cond_mean[cond,2] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp2 < cutoff),]$named,
           na.rm=TRUE)
    
    rRates.cond_n[cond,2] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp2 < cutoff ),])[1]
    
  } else {
    rRates.cond_mean[cond,] <- 
      mean(data_trim[data_trim$condition==cond,]$named,
           na.rm=TRUE)
    
    rRates.cond_n[cond,] <- 
      dim(data_trim[data_trim$condition==cond,])[1]
  }
  
  # var = n*p*(1-p)
  rRates.cond_sem[cond,] <-
    sqrt(rRates.cond_n[cond,] * rRates.cond_mean[cond,] * 
           (1- rRates.cond_mean[cond,])) / 
    sqrt(rRates.cond_n[cond,])
  
}

# look at 2afc rates for pas < 3, collapsed across subs
afcRates.cond_mean = matrix(0,nrow=nConds,ncol=2)
afcRates.cond_sem = matrix(0,nrow=nConds,ncol=2)
afcRates.cond_n = matrix(0,nrow=nConds,ncol=2)
for (cond in 1:nConds) {
  
  if (cond == 3){
    afcRates.cond_mean[cond,1] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp < cutoff),]$afc,
           na.rm=TRUE)
    
    afcRates.cond_n[cond,1] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp < cutoff ),])[1]
    
    # second presentation
    afcRates.cond_mean[cond,2] <- 
      mean(data_trim[data_trim$condition==cond &
                       (data_trim$studyResp2 < cutoff),]$afc,
           na.rm=TRUE)
    
    afcRates.cond_n[cond,2] <- 
      dim(data_trim[data_trim$condition==cond & 
                      (data_trim$studyResp2 < cutoff ),])[1]
    
  } else {
    afcRates.cond_mean[cond,] <- 
      mean(data_trim[data_trim$condition==cond,]$afc,
           na.rm=TRUE)
    
    afcRates.cond_n[cond,] <- 
      dim(data_trim[data_trim$condition==cond,])[1]
  }
  
  # var = n*p*(1-p)
  afcRates.cond_sem[cond,] <-
    sqrt(afcRates.cond_n[cond,] * afcRates.cond_mean[cond,] * 
           (1- rRates.cond_mean[cond,])) / 
    sqrt(afcRates.cond_n[cond,])
  
}

```


```{r,echo=FALSE}
# code for state trace plots

par(mfrow=c(1,1))
new <- plot(afcRates.cond_mean[,1],rRates.cond_mean[,1]
            , xlim = c(0,1)
            , ylim = c(0,1)
            , col = cols
            , xlab = 'prop 2afc correct'
            , ylab = 'recall rate'
            , main = 'PAS < cutoff (firstPresent), subs > 50% respond'
)
legend("topleft", legend = studyConds,
       col=cols,pch = 1,bty="n")


par(mfrow=c(1,1))
new <- plot(afcRates.cond_mean[,2],rRates.cond_mean[,2]
     , xlim = c(0,1)
     , ylim = c(0,1)
     , col = cols
     , xlab = 'prop 2afc correct'
     , ylab = 'recall rate'
     , main = 'PAS < cutoff (secondPresent), subs > 50% respond'
)
legend("topleft", legend = studyConds,
       col=cols,pch = 1,bty="n")

```

```{r}
rRates.cond_sem
afcRates.cond_sem

```

next, look at the state traces by subject

```{r,echo=FALSE}
rRates_sub.cond_mean = array(0,dim=c(nConds,nSubs,2))
rRates_sub.cond_sem = array(0,dim=c(nConds,nSubs,2))
rRates_sub.cond_n = array(0,dim=c(nConds,nSubs,2))
for (cond in 1:nConds) {
  for (sub in 1:nSubs){
    
    if (cond == 3){
      rRates_sub.cond_mean[cond,sub,1] <- 
        mean(data_trim[data_trim$condition==cond &
                         (data_trim$studyResp < cutoff)
                          & data_trim$subject==sub,]$named,
             na.rm=TRUE)
      
      rRates_sub.cond_n[cond,sub,1] <- 
        dim(data_trim[data_trim$condition==cond & 
                        (data_trim$studyResp < cutoff)
                         & data_trim$subject==sub,])[1]
      
      # second presentation
      rRates_sub.cond_mean[cond,sub,2] <- 
        mean(data_trim[data_trim$condition==cond &
                         (data_trim$studyResp2 < cutoff)
                       & data_trim$subject==sub,]$named,
             na.rm=TRUE)
      
      rRates_sub.cond_n[cond,sub,2] <- 
        dim(data_trim[data_trim$condition==cond & 
                        (data_trim$studyResp2 < cutoff)
                      & data_trim$subject==sub,])[1]
      
    } else {
      rRates_sub.cond_mean[cond,sub,] <- 
        mean(data_trim[data_trim$condition==cond
                       & data_trim$subject==sub,]$named,
             na.rm=TRUE)
      
      rRates_sub.cond_n[cond,sub,] <- 
        dim(data_trim[data_trim$condition==cond
                      & data_trim$subject==sub,])[1]
    }
    
    # var = n*p*(1-p)
    rRates_sub.cond_sem[cond,sub,1] <-
      sqrt(rRates_sub.cond_n[cond,sub,1] * rRates_sub.cond_mean[cond,sub,1] * 
             (1- rRates_sub.cond_mean[cond,sub,1])) / 
      sqrt(rRates_sub.cond_n[cond,sub,1])
    
    # second present
    rRates_sub.cond_sem[cond,sub,2] <-
      sqrt(rRates_sub.cond_n[cond,sub,2] * rRates_sub.cond_mean[cond,sub,2] * 
             (1- rRates_sub.cond_mean[cond,sub,2])) / 
      sqrt(rRates_sub.cond_n[cond,sub,2])
  }
}

# look at 2afc rates for pas < 3, collapsed across subs
afcRates_sub.cond_mean = array(0,dim=c(nConds,nSubs,2))
afcRates_sub.cond_sem = array(0,dim=c(nConds,nSubs,2))
afcRates_sub.cond_n = array(0,dim=c(nConds,nSubs,2))
for (cond in 1:nConds) {
  for(sub in 1:nSubs){
    if (cond == 3){
      afcRates_sub.cond_mean[cond,sub,1] <- 
        mean(data_trim[data_trim$condition==cond &
                         (data_trim$studyResp < cutoff)
                       & data_trim$subject==sub,]$afc,
             na.rm=TRUE)
      
      afcRates_sub.cond_n[cond,sub,1] <- 
        dim(data_trim[data_trim$condition==cond & 
                        (data_trim$studyResp < cutoff )
                      & data_trim$subject==sub,])[1]
      
      # second present
      afcRates_sub.cond_mean[cond,sub,2] <- 
        mean(data_trim[data_trim$condition==cond &
                         (data_trim$studyResp2 < cutoff)
                       & data_trim$subject==sub,]$afc,
             na.rm=TRUE)
      
      afcRates_sub.cond_n[cond,sub,2] <- 
        dim(data_trim[data_trim$condition==cond & 
                        (data_trim$studyResp2 < cutoff )
                      & data_trim$subject==sub,])[1]
      
    } else {
      afcRates_sub.cond_mean[cond,sub,] <- 
        mean(data_trim[data_trim$condition==cond
                       & data_trim$subject==sub,]$afc,
             na.rm=TRUE)
      
      afcRates_sub.cond_n[cond,sub,] <- 
        dim(data_trim[data_trim$condition==cond
                      & data_trim$subject==sub,])[1]
    }
    
    # var = n*p*(1-p)
    afcRates_sub.cond_sem[cond,sub,1] <-
      sqrt(afcRates_sub.cond_n[cond,sub,1] * afcRates_sub.cond_mean[cond,sub,1] * 
             (1- rRates_sub.cond_mean[cond,sub,1])) / 
      sqrt(afcRates_sub.cond_n[cond,sub,1])
    
    # second present
    afcRates_sub.cond_sem[cond,sub,2] <-
      sqrt(afcRates_sub.cond_n[cond,sub,2] * afcRates_sub.cond_mean[cond,sub,2] * 
             (1- rRates_sub.cond_mean[cond,sub,2])) / 
      sqrt(afcRates_sub.cond_n[cond,sub,2])
  }
}

```


**first presentation**

```{r,echo=FALSE}
# code for plots

par(mfrow=c(2,3))
for (sub in 1:nSubs){
  
  plot(afcRates_sub.cond_mean[,sub,1],rRates_sub.cond_mean[,sub,1]
       , xlim = c(0,1)
       , ylim = c(0,1)
       , col = cols
       , xlab = 'prop 2afc correct'
       , ylab = 'recall rate'
       , main = c('sub', as.character(sub))
  )
  #legend("topleft", legend = studyConds,
   #      col=cols,pch = 1,bty="n")
  
}

```

**second presentation**

```{r,echo=FALSE}
# code for plots

par(mfrow=c(2,3))
for (sub in 1:nSubs){
  
  plot(afcRates_sub.cond_mean[,sub,2],rRates_sub.cond_mean[,sub,2]
       , xlim = c(0,1)
       , ylim = c(0,1)
       , col = cols
       , xlab = 'prop 2afc correct'
       , ylab = 'recall rate'
       , main = c('sub', as.character(sub))
  )
  #legend("topleft", legend = studyConds,
   #      col=cols,pch = 1,bty="n")
  
}

```


```{r,echo=FALSE,warning=FALSE}
pas.mean_cfs.item = matrix(999,nrow=nPresent,ncol=nItems)
pas.sem_cfs.item = matrix(999,nrow=nPresent,ncol=nItems)
pas.n_cfs.item = matrix(999,nrow=nPresent,ncol=nItems)
for (item in 1:nItems) {
  
  # first present
  pas.mean_cfs.item[1,item] <- 
    mean(data[data$condition==3
              & data$whichItem==item,]$studyResp-1,
         na.rm=TRUE)
  
  pas.n_cfs.item[1,item] <- 
    dim(data[data$condition==3
             & data$whichItem==item,])[1]
  
  # var = n*p*(1-p)
  pas.sem_cfs.item[1,item] <-
    sqrt(pas.n_cfs.item[1,item] * 
           pas.mean_cfs.item[1,item] * 
           (1- pas.mean_cfs.item[1,item])) / 
    sqrt(pas.n_cfs.item[1,item])
  
  # second present
  pas.mean_cfs.item[2,item] <- 
    mean(data[data$condition==3
              & data$whichItem==item,]$studyResp2-1,
         na.rm=TRUE)
  
  pas.n_cfs.item[2,item] <- 
    dim(data[data$condition==3
             & data$whichItem==item,])[1]
  
  pas.sem_cfs.item[2,item] <-
    sqrt(pas.n_cfs.item[2,item] * 
           pas.mean_cfs.item[2,item] * 
           (1- pas.mean_cfs.item[2,item])) / 
    sqrt(pas.n_cfs.item[2,item])
}

pas_item_plot = matrix(0,nrow=nPresent,ncol=nItems)
for (trl in 1:nTrials){
  if(!is.na(pas.mean_cfs.item[,trl])){
    pas_item_plot[,trl] <- pas.mean_cfs.item[,trl]
  }
}


```

```{r,echo=FALSE,warning=FALSE}
# par(mfrow=c(1,1))
# df <- data.frame(first = na.omit(pas.mean_cfs.item[1,]),second = na.omit(pas.mean_cfs.item[2,]))
# numPlot<-ggplot(data = df,aes(x = first,y = second)) + stat_sum(aes(size = ..n..))
# numPlot + ggtitle("mean PAS of items under cfs")


```

```{r,echo=FALSE,warning=FALSE}
pas.mean_cfs.item = array(999,c(nPresent,nSubs,nItems))
pas.n_cfs.item = array(999,c(nPresent,nSubs,nItems))
for (sub in 1:nSubs){
  for (item in 1:nItems) {
    
    if (data[data$whichItem==item
             & data$subject==sub
             ,]$condition==3){
      
      # first present
      pas.mean_cfs.item[1,sub,item] <- 
        data[data$condition==3
             & data$subject==sub
             & data$whichItem==item,]$studyResp-1
      
      pas.n_cfs.item[1,sub,item] <- 
        dim(data[data$condition==3
                 & data$subject==sub
                 & data$whichItem==item,])[1]
      
      
      # second present
      pas.mean_cfs.item[2,sub,item] <- 
        data[data$condition==3
             & data$subject==sub
             & data$whichItem==item,]$studyResp2-1
      
      pas.n_cfs.item[2,sub,item] <- 
        dim(data[data$condition==3
                 & data$subject==sub
                 & data$whichItem==item,])[1]
    }
  }
  
}

pas_sub_item_plot = array(999,c(nPresent,50*nSubs))
item = 0
for (sub in 1:nSubs){
  for (trl in 1:nItems){
    
    if((pas.mean_cfs.item[,sub,trl])!=999){
      item = item+1
      pas_sub_item_plot[,item] <- pas.mean_cfs.item[,sub,trl]
    }
  }
}


```


```{r,echo=FALSE,warning=FALSE}
par(mfrow=c(1,1))
df <- data.frame(first = pas_sub_item_plot[1,]
                 ,second = pas_sub_item_plot[2,]
                 ,sub=rep(1:6,each=50))

numPlot<-ggplot(data = df,aes(x = first,y = second)) + stat_sum(aes(size = ..n..))
numPlot + ggtitle("num(PAS 2 & PAS 1) of items under cfs, all subs")


```

```{r, echo=FALSE,warning=FALSE}
pasCondi.mean.item = array(999,c(nSubs,nPAS,nItems))
pasCondi.n.item = array(999,c(nSubs,nPAS,nItems))
for (sub in 1:nSubs){
  for (pas in 1:nConds){
    for (item in 1:nItems) {
      
      if (length(data[data$whichItem==item
                      & data$subject==sub
                      & data$condition==3
                      ,]$studyResp==pas)!=0 
          && data[data$whichItem==item
                 & data$subject==sub
                 & data$condition==3
                 ,]$studyResp==pas) {
        
        
        # given first resp of pas, what was second?
        pasCondi.mean.item[sub,pas,item] <- 
          data[data$studyResp==pas
               & data$condition==3
               & data$subject==sub
               & data$whichItem==item,]$studyResp2-1
        
        pasCondi.n.item[sub,pas,item] <- 
          dim(data[data$studyResp==pas
                   & data$condition==3
                   & data$subject==sub
                   & data$whichItem==item,])[1]
        
      }
    }
  }
}

pas_condi_plot = array(999,c(50*nSubs,nPAS))
item = 0
for (sub in 1:nSubs){
  for (pas in 1:nPAS){
    for (trl in 1:nItems){
      
      if(!is.na(pasCondi.mean.item[sub,pas,trl])){
        if((pasCondi.mean.item[sub,pas,trl])!=999){
          item = item+1
          pas_condi_plot[item,pas] <- pasCondi.mean.item[sub,pas,trl]
        }
      }
    }
  }
}

# final form?
tally <- array(0,c(nPAS,nPAS))
sum(pas_condi_plot[,1]==3)

for (pas in 1:nPAS){
  for(sec in 1:nPAS){
  tally[pas,sec] <- sum(pas_condi_plot[,pas]==sec-1)
  }
}


barplot(t(tally)
        , beside = TRUE
        , main = "num(PAS_2 | PAS_1)"
        , legend.text = c('to 0', 'to 1', 'to 2', 'to 3')
        , args.legend = list(x="topleft")
        , names.arg = c('0', '1', '2', '3')
)

tally_prop <- tally/rowSums(tally)

```

In the following graph, note that the highest of each group of bars shifts one bar to the right for each gropu (0-3). This says that, for a PAS of 3 on the first presentation, the most likely PAS on the second is 3. Similarly, for a PAS of 2 on the first presentation, the most likely is a 2 on the second (followed by a 1). For 1 on the first, mostly likely is a second 1 (followed by 2). For 0, the most likely is split between 0 and 1.
```{r,echo=FALSE,warning=FALSE}
barplot(t(tally_prop)
        , beside = TRUE
        , main = "p(PAS_2 | PAS_1)"
        , ylim = c(0,1)
        , legend.text = c('to 0', 'to 1', 'to 2', 'to 3')
        , args.legend = list(x="topleft")
        , names.arg = c('0', '1', '2', '3')
)


```
